---
title: "Run ECOMOD"
author: "Alexa Varah"
date: "2023-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Set up
## 1.1. Load packages

```{r}
library(tidyverse) # for easy data manipulation; includes dplyr, ggplot & more
library(readxl) # for reading in Excel workbooks / spreadsheets
```


## 1.2. Load ECOMOD
File '01. Load ECOMOD.R' contains the ECOMOD function used here.
``` {r ECOMOD, purl=FALSE}
source("01. Load ECOMOD_2019 prices_2023-02-07.R")
```

# 2. MIT
Because there are crops in the Farmer Focus strategies that ECOMOD can't model (e.g. spring oats), we read in two versions of the FF strategies. One version has yield set to 'actual', in which average yields for spring oats are given. The second version has yield set to 'estimate', so ECOMOD will estimate yields.

## 2.1. Make input files
```{r load-tidy-MIT}
## Read in the raw data.
mit_est = read_xlsx("../data/ECOMOD_InputData_MIT.xlsx",1) %>% 
  select(-"lookup_ref") %>%  # remove 'lookup_ref' column
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) # soil texture needs 2 decimal places

mit_act = read_xlsx("../data/ECOMOD_InputData_MIT.xlsx",2) %>% 
  select(-"lookup_ref") %>%  # remove 'lookup_ref' column
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) # soil texture needs 2 decimal places

## Create input files for each black-grass density state

# LOW / ABSENT
mit_l_est <- mit_est %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>%
  #select(-X) %>% # remove extra 'row identifier' column added by R when reading in the file
  data.frame()

mit_l_act <- mit_act %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>% 
  #select(-X) %>% # remove extra 'row identifier' column added by R when reading in the file
  data.frame()

# MEDIUM
mit_m_est = mit_l_est %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

mit_m_act = mit_l_act %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

# HIGH
mit_h_est = mit_l_est %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "high"))) %>% 
  data.frame()

mit_h_act = mit_l_act %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "high"))) %>% 
  data.frame()

# VERY HIGH
mit_v_est = mit_l_est %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "veryhigh"))) %>% 
  data.frame()

mit_v_act = mit_l_act %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "veryhigh"))) %>% 
  data.frame()
```


## 2.2. Run ECOMOD - LOW / ABSENT density
### 2.2.1. Run ECOMOD, low density, yield = "estimate" 
Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-lowden-est}
fn = "../output/mit_ECOMOD_output_L_estimate.csv" # name the output file

# Replace spring oats (not included in ECOMOD) 
fd = mit_l_est %>% 
  mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
rm(mit_l_est)
```

### 2.2.2. Run ECOMOD, low density, yield = "actual"
Set up input file (only need to run the rows containing spring oats). Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-lowden-act}
fn = "../output/mit_ECOMOD_output_L_actual.csv" # name the output file

fd = mit_l_act %>% 
  # Extract just the spring oats rows:
  filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="actual",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage) 
rm(fn)
rm(fd)
rm(mfm)
rm(mit_l_act)
```

### 2.2.3. Combine 'actual' and 'estimate' output
Add the 'actual' spring oat output into the 'estimate' output file.
```{r combine-est-act-MIT-lowden}
# Read in the output obtained from ECOMOD
est_l <- read.csv('../output/mit_ECOMOD_output_L_estimate.csv', header=T)
act_l <- read.csv('../output/mit_ECOMOD_output_L_actual.csv', header=T) # this only has rows containing spring oats

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_l_1to4 <- act_l %>% 
  filter(Field_no %in% c(1,2,3,4)) %>% 
  select(!Field_no)

est_l_to_merge <- est_l %>% 
  select(!Field_no)

low_den_output1 <- rows_update(
  est_l_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_l_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_l_5to6 <- act_l %>% 
  filter(Field_no %in% c(5,6)) %>% 
  select(!Field_no)

low_den_output <- rows_update(
  low_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_l_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(low_den_output,'../output/mit_ECOMOD_output_L_combined.csv')

rm(act_l_1to4)
rm(est_l_to_merge)
rm(low_den_output1)
rm(act_l_5to6)
rm(act_l)
rm(est_l)
```

## 2.3. Run ECOMOD - MEDIUM density
### 2.3.1. Run ECOMOD, medium density, yield = "estimate"
Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-mediumden-est}
fn = "../output/mit_ECOMOD_output_M_estimate.csv" # name the output file

fd = mit_m_est %>% 
  mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()

fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage) 
rm(fn)
rm(fd)
rm(mfm)
rm(mit_m_est)
```

### 2.3.2. Run ECOMOD, medium density, yield = "actual"
Set up input file (only need to run the rows containing spring oats). Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-mediumden-act}
fn = "../output/mit_ECOMOD_output_M_actual.csv" # name the output file

fd = mit_m_act %>% 
  filter_all(any_vars(grepl("springoats", .))) %>% # extract spring oats rows
  mutate_at(vars(crop1:crop6), # replace spring oats with spring barley
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="actual",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage) 
rm(fn)
rm(fd)
rm(mfm)
rm(mit_m_act)
```

### 2.3.3. Combine 'actual' and 'estimate' output
Add the 'actual' spring oat output into the 'estimate' output file.
```{r combine-est-act-MIT-mediumden}
# Read in the output obtained from ECOMOD
est_m <- read.csv('../output/mit_ECOMOD_output_M_estimate.csv', header=T)
act_m <- read.csv('../output/mit_ECOMOD_output_M_actual.csv', header=T) # this only has rows containing spring oats

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_m_1to4 <- act_m %>% 
  filter(Field_no %in% c(1,2,3,4)) %>% 
  select(!Field_no)

est_m_to_merge <- est_m %>% 
  select(!Field_no)

med_den_output1 <- rows_update(
  est_m_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_m_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_m_5to6 <- act_m %>% 
  filter(Field_no %in% c(5,6)) %>% 
  select(!Field_no)

med_den_output <- rows_update(
  med_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_m_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(med_den_output,'../output/mit_ECOMOD_output_M_combined.csv')

rm(act_m_1to4)
rm(est_m_to_merge)
rm(med_den_output1)
rm(act_m_5to6)
rm(act_m)
rm(est_m)
```

## 2.4. Run ECOMOD - HIGH density
### 2.4.1. Run ECOMOD, high density, yield = "estimate"
Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-highden-est}
fn = "../output/mit_ECOMOD_output_H_estimate.csv" # name the output file

fd = mit_h_est %>% 
  mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()

fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage) 
rm(fn)
rm(fd)
rm(mfm)
```


### 2.4.2. Run ECOMOD, high density, yield = "actual"
Set up input file (only need to run the rows containing spring oats). Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-highden-act}
fn = "../output/mit_ECOMOD_output_H_actual.csv" # name the output file

fd = mit_h_act %>% 
  filter_all(any_vars(grepl("springoats", .))) %>% # extract spring oats rows
  mutate_at(vars(crop1:crop6), # replace spring oats with spring barley
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="actual",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage) 
rm(fn)
rm(fd)
rm(mfm)
```

### 2.4.3. Combine 'actual' and 'estimate' output
Add the 'actual' spring oat output into the 'estimate' output file.
```{r combine-est-act-MIT-highden}
# Read in the output obtained from ECOMOD
est_h <- read.csv('../output/mit_ECOMOD_output_H_estimate.csv', header=T)
act_h <- read.csv('../output/mit_ECOMOD_output_H_actual.csv', header=T) # this only has rows containing spring oats

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_h_1to4 <- act_h %>% 
  filter(Field_no %in% c(1,2,3,4)) %>% 
  select(!Field_no)

est_h_to_merge <- est_h %>% 
  select(!Field_no)

high_den_output1 <- rows_update(
  est_h_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_h_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_h_5to6 <- act_h %>% 
  filter(Field_no %in% c(5,6)) %>% 
  select(!Field_no)

high_den_output <- rows_update(
  high_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_h_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(high_den_output,'../output/mit_ECOMOD_output_H_combined.csv')

rm(act_h_1to4)
rm(est_h_to_merge)
rm(high_den_output1)
rm(act_h_5to6)
rm(mit_h_act)
rm(mit_h_est)
rm(act_h)
rm(est_h)
```

## 2.5. Run ECOMOD - VERY HIGH density
### 2.5.1. Run ECOMOD, very high density, yield = "estimate"
Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-veryhighden-est}
fn = "../output/mit_ECOMOD_output_V_estimate.csv" # name the output file

fd = mit_v_est %>% 
  mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()

fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage) 
rm(fn)
rm(fd)
rm(mfm)
```

### 2.5.2. Run ECOMOD, high density, yield = "actual" 
Set up input file (only need to run the rows containing spring oats). Replace spring oats with spring barley and ensure soil is to two decimal places or ECOMOD won't run.
```{r runECOMOD-MIT-veryhighden-act}
fn = "../output/mit_ECOMOD_output_V_actual.csv" # name the output file

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil 
# is to two decimal places or ECOMOD won't run.
fd = mit_v_act %>% 
  filter_all(any_vars(grepl("springoats", .))) %>% # extract spring oats rows
  mutate_at(vars(crop1:crop6), # replace spring oats with spring barley
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()

fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="actual",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage) 
rm(fn)
rm(fd)
rm(mfm)
```

### 2.5.3. Combine 'actual' and 'estimate' output
Add the 'actual' spring oat output into the 'estimate' output file.
```{r combine-est-act-MIT-veryhighden}
# Read in the output obtained from ECOMOD
est_v <- read.csv('../output/mit_ECOMOD_output_V_estimate.csv', header=T)
act_v <- read.csv('../output/mit_ECOMOD_output_V_actual.csv', header=T) # this only has rows containing spring oats

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_v_1to4 <- act_v %>% 
  filter(Field_no %in% c(1,2,3,4)) %>% 
  select(!Field_no)

est_v_to_merge <- est_v %>% 
  select(!Field_no)

vhigh_den_output1 <- rows_update(
  est_v_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_v_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_v_5to6 <- act_v %>% 
  filter(Field_no %in% c(5,6)) %>% 
  select(!Field_no)

vhigh_den_output <- rows_update(
  vhigh_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  select(act_v_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(vhigh_den_output,'../output/mit_ECOMOD_output_V_combined.csv')

rm(act_v_1to4)
rm(est_v_to_merge)
rm(vhigh_den_output1)
rm(act_v_5to6)
rm(mit_v_act)
rm(mit_v_est)
rm(act_v)
rm(est_v)

rm(mit_l_act)
rm(mit_l_est)
rm(mit_act)
rm(mit_est)
```

# 3. BAU
## 3.1. Make input files
```{r load-tidy-BAU}
# Read in file and sort out a few things initially.
bau_econdata = read_xlsx("../data/ECOMOD_InputData_BAU.xlsx") %>% 
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) %>%  # soil texture needs 2 decimal places
  # replace density and resistance abbreviations with even shorter forms:
  mutate(
    farm_id = gsub('L-Dsty.L-Res', 'LD-LR', farm_id), 
    farm_id = gsub('L-Dsty.H-Res', 'LD-HR', farm_id),
    farm_id = gsub('H-Dsty.H-Res', 'HD-HR', farm_id),
    farm_id = gsub('\\.', '_', farm_id), # replace . with _
  )

# Insert the additional scenarios that Rob G can run. 
# He can differentiate all density states.
# LD-LR becomes LD-LR and MD-LR
# LD-HR becomes LD-HR and MD-HR
# HD-HR becomes HD-HR and VD-HR

# create new rows to be added
bau_insert.df <- bau_econdata %>% 
  mutate(
    farm_id = gsub('LD-LR', 'MD-LR', farm_id), # replace LD-LR with MD-LR
    farm_id = gsub('LD-HR', 'MD-HR', farm_id),
    farm_id = gsub('HD-HR', 'VD-HR', farm_id)
  )
    
# join the two data frames
bau_out.df <- rbind(bau_econdata, bau_insert.df)

# re-order so that new rows are inserted every other row
n <- nrow(bau_econdata)
bau_econ.input.data <- bau_out.df[kronecker(1:n, c(0, n), "+"), ]

## Create input files for each black-grass density state

# LOW / ABSENT
bau_l <- bau_econ.input.data %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>%
  data.frame()

# MEDIUM
bau_m <- bau_l %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

# HIGH
bau_h = bau_m %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "medium", "high"))) %>% 
  data.frame()

# VERY HIGH
bau_v = bau_h %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "high", "veryhigh"))) %>% 
  data.frame()
```

## 3.2. Run ECOMOD
### 3.2.1. Run ECOMOD - LOW / ABSENT density
```{r runECOMOD-BAU-lowden}
fn = "../output/bau_ECOMOD_output_L.csv" # name the output file
fd = bau_l
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

### 3.2.2. Run ECOMOD - MEDIUM density
```{r runECOMOD-BAU-mediumden}
fn = "../output/bau_ECOMOD_output_M.csv" # name the output file
fd = bau_m
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

### 3.2.3. Run ECOMOD - HIGH density
```{r runECOMOD-BAU-highden}
fn = "../output/bau_ECOMOD_output_H.csv" # name the output file
fd = bau_h
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

### 3.2.4. Run ECOMOD - VERY HIGH density
```{r runECOMOD-BAU-veryhighden}
fn = "../output/bau_ECOMOD_output_V.csv" # name the output file
fd = bau_v
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

### 3.2.5. Clean up
```{r BAU-clean-up}
rm(bau_l)
rm(bau_m)
rm(bau_h)
rm(bau_v)
rm(bau_econdata)
rm(bau_insert.df)
rm(bau_out.df)
rm(bau_econ.input.data)
rm(n)
rm(low_den_output)
rm(med_den_output)
rm(high_den_output)
rm(vhigh_den_output)
```



# 4. CWW
## 4.1. Make input files 
```{r load-tidy-CWW}
#cww_econdata = read_xlsx("../data/InputData_CWW_ECOMOD&CFT_2021-12-02.xlsx",5) %>%
cww_econdata = read_xlsx("../data/ECOMOD_InputData_CWW.xlsx") %>% 
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) %>% # soil texture needs 2 decimal places
  # replace density and resistance abbreviations with even shorter forms:
  mutate(
    farm_id = gsub('L-Dsty.L-Res', 'LD-LR', farm_id), 
    farm_id = gsub('L-Dsty.H-Res', 'LD-HR', farm_id),
    farm_id = gsub('H-Dsty.H-Res', 'HD-HR', farm_id),
    farm_id = gsub('\\.', '_', farm_id), # replace . with _
  )
  
# Insert the additional scenarios that Rob G can run. 
# He can differentiate all density states.
# LD-LR becomes LD-LR and MD-LR
# LD-HR becomes LD-HR and MD-HR
# HD-HR becomes HD-HR and VD-HR

# create new rows to be added
cww_insert.df <- cww_econdata %>% 
  mutate(
    farm_id = gsub('LD-LR', 'MD-LR', farm_id), # replace LD-LR with MD-LR
    farm_id = gsub('LD-HR', 'MD-HR', farm_id),
    farm_id = gsub('HD-HR', 'VD-HR', farm_id)
  )

# join the two dataframes
cww_out.df <- rbind(cww_econdata, cww_insert.df)

# re-order so that new rows are inserted every other row
n <- nrow(cww_econdata)
cww_econ.input.data <- cww_out.df[kronecker(1:n, c(0, n), "+"), ]


## Create input files for each black-grass density state

# LOW / ABSENT
cww_l <- cww_econ.input.data %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>%
  data.frame()

# MEDIUM
cww_m <- cww_l %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

# HIGH
cww_h = cww_m %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "medium", "high"))) %>% 
  data.frame()

# VERY HIGH
cww_v = cww_h %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "high", "veryhigh"))) %>% 
  data.frame()
```


## 4.2. Run ECOMOD - LOW / ABSENT density
```{r runECOMOD-CWW-lowden}
fn = "../output/cww_ECOMOD_output_L.csv" # name the output file
fd = cww_l
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

## 4.3. Run ECOMOD - MEDIUM density
```{r runECOMOD-CWW-mediumden}
fn = "../output/cww_ECOMOD_output_M.csv" # name the output file
fd = cww_m
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

## 4.4. Run ECOMOD - HIGH density
```{r runECOMOD-CWW-highden}
fn = "../output/cww_ECOMOD_output_H.csv" # name the output file
fd = cww_h
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

## 4.5. Run ECOMOD - VERY HIGH density
```{r runECOMOD-CWW-veryhighden}
fn = "../output/cww_ECOMOD_output_V.csv" # name the output file
fd = cww_v
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD(filename=fn,
                        farmdata=fd,
                        default=NULL,farm="multiple",soil=2.5,
                        rotlength=6,rotprob=1/6,
                        crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
                        bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
                        blackgrass,cropprice,cropyield,yieldoption="estimate",
                        Nfertprice,Pfertprice,Kfertprice,seedprice,
                        herbprice,glyphosateprice,machsize,fuelprice,labourwage)
rm(fn)
rm(fd)
rm(mfm)
```

## 4.6. Clean up
```{r CWW-clean-up}
rm(cww_l)
rm(cww_m)
rm(cww_h)
rm(cww_v)
rm(cww_econdata)
rm(cww_insert.df)
rm(cww_out.df)
rm(cww_econ.input.data)
rm(n)
```


