---
title: "Tidy density simulation data"
author: "Alexa Varah"
date: "2022-11-22"
output: html_document
---


# 1. Intro
In Rob's simulated density data, 'mds' is "the expectation of the density state, i.e. the sum of the predicted probability of each state multiplied by each state value."

The initial density distributions for each state are as follows:   
* "very high"  <- matrix(c(0.1,0.1,0.2,0.3,0.3),ncol=5)  
* "high"       <- matrix(c(0.2,0.2,0.2,0.2,0.2),ncol=5)  
* "medium"     <- matrix(c(0.2,0.2,0.6,0,0),ncol=5)  
* "low"        <- matrix(c(0.2,0.8,0,0,0),ncol=5)  


# 2. Set-up
## 2.1. Load packages
```{r}
rm(list=ls())
library(tidyverse) 
```

## 2.2. Load data
```{r}
# simulated density data:
res <- readRDS("../data/2023-02-13_simulation_results.rds")
# simulated density with all fields run at initial high density:
res_hd <- readRDS("../data/2023-02-13_simulation_results_HD.rds")
# simulated density with all fields run at initial very high density:
res_vd <- readRDS("../data/2023-02-13_simulation_results_VD.rds")
```

# 3. Tidy main data
## 3.1.Tidy

N.B. in the raw data "iter" correctly represents year so use that rather than 'year'.  

```{r}
res_tidy <- res %>%
  subset(select=c(imp,strategy,iter:v)) %>% # pull out the columns we want
  dplyr::mutate(iter = as.numeric(iter), # make 'iter' numeric
                #iter = iter -1, # replace 1 with 0, 2 with 1, etc.
                strategy = str_replace_all(strategy, "FF","MIT")
                ) %>%  
  rename(year = iter) %>% # rename 'iter' as 'year'
  separate(strategy,into = c("scenario","initden", "initres", 
                             "region", "soiltype"),sep = "_") %>% 
  dplyr::mutate( 
    scenario = factor(scenario),
    region_temp = dplyr::recode(region, # rename levels of 'region'
                                "north" = "n",
                                "central" = "c",
                                "east" = "e"),
    soiltype = factor(soiltype),
    region = factor(region, # specify order of levels
                    levels = c("north", "central", "east")),
    region_temp = dplyr::recode(region, # rename levels of 'region'
                           "north" = "n",
                           "central" = "c",
                           "east" = "e"),
    soil_temp = dplyr::recode(soiltype,  # rename levels of 'soiltype'
                              "heavy" = "h",
                              "medium" = "m",
                              "light" = "l"),
    # create column of initial density and resistance
    initdenres = paste(initden, initres, sep = "-"),
    initdenres = factor(initdenres, # specify order of levels
                        levels = c("VD-HR", "HD-HR", "MD-HR", 
                                   "MD-LR", "LD-HR", "LD-LR")) , 
    # create column of initial conditions
    initcondit = paste(region_temp, soil_temp, initdenres, sep = "_"),
    # specify order of levels so later plots are in correct order:
    initcondit = factor(initcondit, levels = c(
      "n_h_VD-HR", "n_m_VD-HR", "n_l_VD-HR", 
      "c_h_VD-HR", "c_m_VD-HR", "c_l_VD-HR",
      "e_h_VD-HR", "e_m_VD-HR", "e_l_VD-HR",
      
      "n_h_HD-HR", "n_m_HD-HR", "n_l_HD-HR",
      "c_h_HD-HR", "c_m_HD-HR", "c_l_HD-HR",
      "e_h_HD-HR", "e_m_HD-HR", "e_l_HD-HR",
      
      "n_h_MD-HR", "n_m_MD-HR", "n_l_MD-HR",
      "c_h_MD-HR", "c_m_MD-HR", "c_l_MD-HR",
      "e_h_MD-HR", "e_m_MD-HR", "e_l_MD-HR",
      
      "n_h_MD-LR", "n_m_MD-LR", "n_l_MD-LR",
      "c_h_MD-LR", "c_m_MD-LR", "c_l_MD-LR",
      "e_h_MD-LR", "e_m_MD-LR", "e_l_MD-LR",
      
      "n_h_LD-HR", "n_m_LD-HR", "n_l_LD-HR",
      "c_h_LD-HR", "c_m_LD-HR", "c_l_LD-HR",
      "e_h_LD-HR", "e_m_LD-HR", "e_l_LD-HR",
      
      "n_h_LD-LR", "n_m_LD-LR", "n_l_LD-LR",
      "c_h_LD-LR", "c_m_LD-LR", "c_l_LD-LR",
      "e_h_LD-LR", "e_m_LD-LR", "e_l_LD-LR")),
   initden = factor(initden),
   initres = factor(initres),
   strategy = factor(paste(scenario, initdenres, region, soiltype, sep="_")),
   joinID = paste(strategy, year, sep="_")
    ) %>% 
  dplyr::select(-c(region_temp, soil_temp)) %>% 
  dplyr::mutate(model_run = "main")
```

## 3.2.Check
Check data is what I expect. 
  
Do I have three scenarios?  
```{r}
levels(res_tidy$scenario)
```

Do I have the correct density-resistance states?
```{r}
levels(res_tidy$initdenres)
```
  
Do all years have the same number of observations?
```{r}
table(res_tidy$year)
```


There should be 54 levels in each scenario: 
MIT  
```{r}
nlevels(res_tidy$initcondit[res_tidy$scenario == "MIT"])
```
  
```{r}
nlevels(res_tidy$initcondit[res_tidy$scenario == "BAU"])
```
  
```{r}
nlevels(res_tidy$initcondit[res_tidy$scenario == "CWW"])
```
  
And there should be 6 reps (i.e. years) for each level. Check none have more than 6 rows.
MIT  
```{r}
res_tidy %>% filter(scenario == "MIT") %>% count(initcondit) %>% filter(n > 6)
```

BAU
```{r}
res_tidy %>% filter(scenario == "BAU") %>% count(initcondit) %>% filter(n > 6)
```
  
CWW
```{r}
res_tidy %>% filter(scenario == "CWW") %>% count(initcondit) %>% filter(n > 6)
```
    
Each combo of scenario and initdenres should have 54 repeats. This is because we run each initial denres (e.g. VD-HR) for each of 3 soil types (h, m, l), 3 regions (n, c, e) , each for a 6 year rotation. Do they?
```{r}
res_tidy %>% count(scenario, initdenres) %>% filter(n > 54)
```
  
Yes, all have 54 and none have more than 54.  

```{r}
#str(res_tidy)
```
  
Everything looks correct.  
  
## 3.3. Save
```{r}
#write.csv(res_tidy,"../output/simulation_results_tidy.csv", row.names = FALSE)
saveRDS(res_tidy, file = "../output/simulation_results_tidy.rds")
```



# 4. Tidy LD-HR data run with initial HD
Because the results of analyses using the original data suggested that it sometimes became financially viable to switch to LD-HR strategies under ‘worst-case’ black-grass densities, I want to estimate the effect on BG density of applying LD-HR strategies to HD-HR fields. So Rob ran the density simulations for LD-HR strategies again but specified initial high densities (in fact he ran all strategies again, but I can filter when needed).

## 4.1. Tidy
```{r}
res_tidy_hd <-  res_hd %>%
  dplyr::select(-step) %>% 
  dplyr::mutate(
    iter = as.numeric(iter), # make 'iter' numeric
    strategy = str_replace_all(strategy, "FF","MIT")
    ) %>%  
  rename(year=iter) %>% # rename 'iter' as 'year'
  dplyr::mutate(
    strategy = factor(strategy),
    strategy_to_keep = strategy,
    strategy_to_keep = str_replace_all(strategy_to_keep, "D_","D-"),
    joinID = paste(strategy_to_keep, year, sep="_")
    ) %>% 
  # create columns to show region, soil type and initial den & res conditions:
  separate(strategy, into=c("scenario","initden", "initres", 
                            "region", "soiltype"),sep = "_") %>% 
  rename(strategy = strategy_to_keep) %>%
  dplyr::mutate(
    region_temp = dplyr::recode(region,  # rename levels of 'region'
                                "north" = "n",
                                "central" = "c",
                                "east" = "e"),
    # create column of initial density and resistance
    soiltype = factor(soiltype),
    region = factor(region, # specify order of levels
                    levels = c("north", "central", "east")),
    region_temp = dplyr::recode(region,  # rename levels of 'region'
                                "north" = "n",
                                "central" = "c",
                                "east" = "e"),
    soil_temp = dplyr::recode(soiltype,  # rename levels of 'region'
                              "heavy" = "h",
                              "medium" = "m",
                              "light" = "l"),
    initdenres = paste(initden, initres, sep = "-"),
    initdenres = factor(initdenres, # specify order of levels
                        levels = c("VD-HR", "HD-HR", "MD-HR", 
                                   "MD-LR", "LD-HR", "LD-LR")) , 
    # create column of initial conditions
    initcondit = paste(region_temp, soil_temp, initdenres, sep = "_"),
    # specify order of levels so later plots are in correct order:
    initcondit = factor(initcondit, levels = c(
      "n_h_VD-HR", "n_m_VD-HR", "n_l_VD-HR", 
      "c_h_VD-HR", "c_m_VD-HR", "c_l_VD-HR",
      "e_h_VD-HR", "e_m_VD-HR", "e_l_VD-HR",
          
      "n_h_HD-HR", "n_m_HD-HR", "n_l_HD-HR",
      "c_h_HD-HR", "c_m_HD-HR", "c_l_HD-HR",
      "e_h_HD-HR", "e_m_HD-HR", "e_l_HD-HR",
          
      "n_h_MD-HR", "n_m_MD-HR", "n_l_MD-HR",
      "c_h_MD-HR", "c_m_MD-HR", "c_l_MD-HR",
      "e_h_MD-HR", "e_m_MD-HR", "e_l_MD-HR",
          
      "n_h_MD-LR", "n_m_MD-LR", "n_l_MD-LR",
      "c_h_MD-LR", "c_m_MD-LR", "c_l_MD-LR",
      "e_h_MD-LR", "e_m_MD-LR", "e_l_MD-LR",
          
      "n_h_LD-HR", "n_m_LD-HR", "n_l_LD-HR",
      "c_h_LD-HR", "c_m_LD-HR", "c_l_LD-HR",
      "e_h_LD-HR", "e_m_LD-HR", "e_l_LD-HR",
          
      "n_h_LD-LR", "n_m_LD-LR", "n_l_LD-LR",
      "c_h_LD-LR", "c_m_LD-LR", "c_l_LD-LR",
      "e_h_LD-LR", "e_m_LD-LR", "e_l_LD-LR")),
    scenario = factor(scenario),
    initden = factor(initden),
    initres = factor(initres)
    ) %>% 
  dplyr::select(-c(region_temp, soil_temp)) %>% 
  dplyr::relocate(c(initdenres, initcondit), .after = v) %>% 
  droplevels()%>% 
  dplyr::mutate(model_run = "all_init_HD")
```

## 4.2. Check
Do I have three scenarios?  
```{r}
levels(res_tidy_hd$scenario)
```

Do all years have the same number of observations?
```{r}
table(res_tidy_hd$year)
```


```{r}
str(res_tidy_hd)
```


## 4.3. Save
```{r}
#write.csv(res_tidy_hd,"../output/simulation_results_tidy_hd.csv", row.names = FALSE)
saveRDS(res_tidy_hd, file = "../output/simulation_results_tidy_hd.rds")
```



# 5. Tidy LD-HR data run with initial VD
Because the results of analyses using the original data suggested that it sometimes became financially viable to switch to LD-HR strategies under ‘worst-case’ black-grass densities, I want to estimate the effect on BG density of applying LD-HR strategies to HD-HR fields. So Rob ran the density simulations for LD-HR strategies again but specified initial high densities.

## 5.1. Tidy

```{r}
res_tidy_vd <-  res_vd %>%
  subset(select=c(imp,strategy,iter:v)) %>% # pull out the columns we want
  dplyr::mutate(
    iter = as.numeric(iter), # make 'iter' numeric
    strategy = str_replace_all(strategy, "FF","MIT")
    ) %>%  
  rename(year=iter) %>% # rename 'iter' as 'year'
  dplyr::filter(!year==0) %>% 
  dplyr::mutate(
    strategy = factor(strategy),
    strategy_to_keep = strategy,
    strategy_to_keep = str_replace_all(strategy_to_keep, "D_","D-"),
    joinID = paste(strategy_to_keep, year, sep="_")
    ) %>% 
  # create columns to show region, soil type and initial den & res conditions:
  separate(strategy, into=c("scenario","initden", "initres", 
                            "region", "soiltype"),sep = "_") %>% 
  rename(strategy = strategy_to_keep) %>%
  dplyr::mutate(
    region_temp = dplyr::recode(region,  # rename levels of 'region'
                                "north" = "n",
                                "central" = "c",
                                "east" = "e"),
    # create column of initial density and resistance
    soiltype = factor(soiltype),
    region = factor(region, # specify order of levels
                    levels = c("north", "central", "east")),
    region_temp = dplyr::recode(region,  # rename levels of 'region'
                                "north" = "n",
                                "central" = "c",
                                "east" = "e"),
    soil_temp = dplyr::recode(soiltype,  # rename levels of 'region'
                              "heavy" = "h",
                              "medium" = "m",
                              "light" = "l"),
    initdenres = paste(initden, initres, sep = "-"),
    initdenres = factor(initdenres, # specify order of levels
                        levels = c("VD-HR", "HD-HR", "MD-HR", 
                                   "MD-LR", "LD-HR", "LD-LR")) , 
    # create column of initial conditions
    initcondit = paste(region_temp, soil_temp, initdenres, sep = "_"),
    # specify order of levels so later plots are in correct order:
    initcondit = factor(initcondit, levels = c(
      "n_h_VD-HR", "n_m_VD-HR", "n_l_VD-HR", 
      "c_h_VD-HR", "c_m_VD-HR", "c_l_VD-HR",
      "e_h_VD-HR", "e_m_VD-HR", "e_l_VD-HR",
          
      "n_h_HD-HR", "n_m_HD-HR", "n_l_HD-HR",
      "c_h_HD-HR", "c_m_HD-HR", "c_l_HD-HR",
      "e_h_HD-HR", "e_m_HD-HR", "e_l_HD-HR",
          
      "n_h_MD-HR", "n_m_MD-HR", "n_l_MD-HR",
      "c_h_MD-HR", "c_m_MD-HR", "c_l_MD-HR",
      "e_h_MD-HR", "e_m_MD-HR", "e_l_MD-HR",
          
      "n_h_MD-LR", "n_m_MD-LR", "n_l_MD-LR",
      "c_h_MD-LR", "c_m_MD-LR", "c_l_MD-LR",
      "e_h_MD-LR", "e_m_MD-LR", "e_l_MD-LR",
          
      "n_h_LD-HR", "n_m_LD-HR", "n_l_LD-HR",
      "c_h_LD-HR", "c_m_LD-HR", "c_l_LD-HR",
      "e_h_LD-HR", "e_m_LD-HR", "e_l_LD-HR",
          
      "n_h_LD-LR", "n_m_LD-LR", "n_l_LD-LR",
      "c_h_LD-LR", "c_m_LD-LR", "c_l_LD-LR",
      "e_h_LD-LR", "e_m_LD-LR", "e_l_LD-LR")),
    scenario = factor(scenario),
    initden = factor(initden),
    initres = factor(initres)
    ) %>% 
  dplyr::select(-c(region_temp, soil_temp)) %>% 
  dplyr::relocate(c(initdenres, initcondit), .after = v) %>% 
  droplevels() %>% 
  dplyr::mutate(model_run = "all_init_VD")
```

## 5.2. Check
Do I have three scenarios?  
```{r}
levels(res_tidy_vd$scenario)
```

Do all years have the same number of observations?
```{r}
table(res_tidy_vd$year)
```

```{r}
str(res_tidy_vd)
```

## 5.3. Save
```{r}
saveRDS(res_tidy_vd, file = "../output/simulation_results_tidy_vd.rds")
```






