---
title: "Visualising the simulated effect of scenario on density"
author: "Alexa Varah"
date: "2022-12-12"
output: html_document
---

# 1. Intro / rationale
This script visualises the simulated effect of scenario on black-grass density. I'm going to look at three aspects of density to see how they respond to scenario:  
  
1. Mean proportion of high and very high density across a 6-year rotation.  
2. Proportion of high and very high density in year 6 (i.e. the final density).  
3. Weighted mean density state across a 6-year rotation.

The initial density distributions that Rob G used for each state are as follows:
"very high"  <- matrix(c(0.1,0.1,0.2,0.3,0.3),ncol=5),
"high"       <- matrix(c(0.2,0.2,0.2,0.2,0.2),ncol=5),
"medium"     <- matrix(c(0.2,0.2,0.6,0,0),ncol=5),
"low"        <- matrix(c(0.2,0.8,0,0,0),ncol=5))

As these are model simulations, I don't need to do any statistical modelling. To show the effect of scenario, I'll look at the proportions of high and very high density at each time step and relate it to scenario (BAU, MIT or CWW). I'll use the proportion of high and very high (hvh) density states because they have a yield & economic impact. Low and medium states don't have an impact on yield so they are unimportant here.  
The alternative would be to use mean density state across the whole field but it isn't very meaningful. For example, a mean state of 3 could signify that the whole field has high density of BG; or it could mean that some of the field is low or medium density and some is very high. These two situations have different implications for field-scale wheat yield.  
  
# 2. Set-up
## 2.1. Load packages
```{r load-packages, message=FALSE}
rm(list=ls())
library(tidyverse) # for easy data manipulation; includes dplyr, ggplot & more
library(ggsignif) # required for function "geom_signif" used in box plots
```

## 2.2. Load data
I will work with the dataset that contains the mean proportion of high and very high density Black-grass in a field each year. Call this `mean_hvh`.
```{r}
density_3dr <- readRDS("../output/density_data_summarised_3dr.rds") 
density_3dr_hd <- readRDS("../output/density_data_summarised_3dr_hd.rds") 
```

## 2.3. Summarize by scenario and region

For each scenario, calculate yearly means.
```{r}
smrz_scenario_3dr <- density_3dr %>% 
  group_by(scenario, year) %>% # grouping factor for sum
  dplyr::mutate(
    #mds           
    mds = mean(mds_mean),
    mds_95ci_l = mds - (1.96 * (sd(mds_mean) / sqrt(length(mds_mean)))),
    mds_95ci_u = mds + (1.96 * (sd(mds_mean) / sqrt(length(mds_mean)))),
    
    #hvh
    hvh = mean(hvh_mean),
    hvh_95ci_l = hvh - (1.96 * (sd(hvh_mean) / sqrt(length(hvh_mean)))),
    hvh_95ci_u = hvh + (1.96 * (sd(hvh_mean) / sqrt(length(hvh_mean)))),
    
    #pdec
    pdec = mean(pdec_mean),
    pdec_95ci_l = pdec - (1.96 * (sd(pdec_mean) / sqrt(length(pdec_mean)))),
    pdec_95ci_u = pdec + (1.96 * (sd(pdec_mean) / sqrt(length(pdec_mean)))),
    
    #pinc
    pinc = mean(pinc_mean),
    pinc_95ci_l = pinc - (1.96 * (sd(pinc_mean) / sqrt(length(pinc_mean)))),
    pinc_95ci_u = pinc + (1.96 * (sd(pinc_mean) / sqrt(length(pinc_mean)))),
    
    # mds diff
    mds_diff = mean(mds_diff_mean),
    mds_diff_95ci_l = mds_diff - (1.96 * (sd(mds_diff_mean) / sqrt(length(mds_diff_mean)))),
    mds_diff_95ci_u = mds_diff + (1.96 * (sd(mds_diff_mean) / sqrt(length(mds_diff_mean)))),
    
    # hvh diff
    hvh_diff = mean(hvh_diff_mean),
    hvh_diff_95ci_l = hvh_diff - (1.96 * (sd(hvh_diff_mean) / sqrt(length(hvh_diff_mean)))),
    hvh_diff_95ci_u = hvh_diff + (1.96 * (sd(hvh_diff_mean) / sqrt(length(hvh_diff_mean))))
    ) %>%
  # retain only one row per scenario-year:
  distinct(scenario, year, .keep_all = TRUE) %>% 
  dplyr::select(scenario, year, mds:hvh_diff_95ci_u)
```


For each scenario and initial den-res state (3 levels), calculate yearly means.
```{r}
smrz_scenario_initDR_3dr <- density_3dr %>% 
  group_by(scenario, year, initDR3) %>% # grouping factor for sum
  dplyr::mutate(
    #mds           
    mds = mean(mds_mean),
    mds_95ci_l = mds - (1.96 * (sd(mds_mean) / sqrt(length(mds_mean)))),
    mds_95ci_u = mds + (1.96 * (sd(mds_mean) / sqrt(length(mds_mean)))),
    
    #hvh
    hvh = mean(hvh_mean),
    hvh_95ci_l = hvh - (1.96 * (sd(hvh_mean) / sqrt(length(hvh_mean)))),
    hvh_95ci_u = hvh + (1.96 * (sd(hvh_mean) / sqrt(length(hvh_mean)))),
    
    #pdec
    pdec = mean(pdec_mean),
    pdec_95ci_l = pdec - (1.96 * (sd(pdec_mean) / sqrt(length(pdec_mean)))),
    pdec_95ci_u = pdec + (1.96 * (sd(pdec_mean) / sqrt(length(pdec_mean)))),
    
    #pinc
    pinc = mean(pinc_mean),
    pinc_95ci_l = pinc - (1.96 * (sd(pinc_mean) / sqrt(length(pinc_mean)))),
    pinc_95ci_u = pinc + (1.96 * (sd(pinc_mean) / sqrt(length(pinc_mean)))),
    
    # mds diff
    mds_diff = mean(mds_diff_mean),
    mds_diff_95ci_l = mds_diff - (1.96 * (sd(mds_diff_mean) / sqrt(length(mds_diff_mean)))),
    mds_diff_95ci_u = mds_diff + (1.96 * (sd(mds_diff_mean) / sqrt(length(mds_diff_mean)))),
    
    # hvh diff
    hvh_diff = mean(hvh_diff_mean),
    hvh_diff_95ci_l = hvh_diff - (1.96 * (sd(hvh_diff_mean) / sqrt(length(hvh_diff_mean)))),
    hvh_diff_95ci_u = hvh_diff + (1.96 * (sd(hvh_diff_mean) / sqrt(length(hvh_diff_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, year, initDR3, .keep_all = TRUE) %>% 
  dplyr::select(scenario, year, initDR3, mds:hvh_diff_95ci_u)
```

#### Save data frame
```{r}
write.csv(smrz_scenario_initDR_3dr, "../output/data for line graph_density.csv", 
          row.names = FALSE)
```


# 3. Plot effect of scenario on BG density

## 3.1. Mean proportion of high and very high density across a 6-year rotation.  
Plot the proportion of a field with high or very high density black-grass at each year in the 6 year rotation.

First, specify the labels for the panels.  
```{r specify-panel-labels-p3}
initDR3.labs <- c("(i) Low density,\n low resistance", "(ii) Low density,\n high resistance", "(iii) High density,\n high resistance") # new
names(initDR3.labs) <- c("LD-LR", "LD-HR", "HD-HR") # original
```

Then specify the plot.
```{r plot-p3}
p3 <- ggplot(smrz_scenario_initDR_3dr, 
       aes(x = year, y = hvh, group = scenario, colour = scenario)) +
  facet_wrap(~initDR3, labeller = labeller(initDR3 = initDR3.labs)) +
  geom_ribbon(aes(ymin = hvh_95ci_l, ymax = hvh_95ci_u, fill = scenario), 
              alpha = 0.1, # controls transparency
              linetype = "blank" # gets rid of upper and lower lines
              ) +
  scale_fill_manual(
    name = "Scenario",
    values = c("#00306F", # BAU, madison blue
               "#00C2F9", # MIT, capri blue
               "#005FCC"  # CWW, royal blue
               )
    ) +
  geom_line() +  
  scale_color_manual(
    name = "Scenario",
    values = c("#00306F", # BAU, madison blue
               "#00C2F9", # MIT, capri blue
               "#005FCC"  # CWW, royal blue
               )
    ) +
  theme_classic() +
  labs(x = "Year in rotation", 
       y = "Proportion of field with economically- \n damaging weed densities") +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    plot.title = element_blank(),
    axis.title=element_text(size=18),
    axis.text.x=element_text(size=rel(1.7)),
    axis.text.y=element_text(size=rel(1.7)),
    legend.title=element_text(size=18),
    legend.text=element_text(size=16),
    strip.background = element_rect(color = "white",
                                    fill = "grey"),# colour of rectangle round region labels
    strip.text = element_text(size = 16)
    ) 

p3
```


## ---

## 3.2. Prophvh in year 6 by scenario & initcondit (no CWW)
Scatter plot of density by 3 init conditions, just BAU and MIT scenarios. Use the `prophvh_3dr` dataset: this contains the mean proportion of squares in high or very high density states, with initial density/resistance states collapsed to three levels.


Specify what you want written in the facet strips.
```{r specify-facets-sp1}
region.labs <- c("Northern England", "Central England", "Eastern England") # new
names(region.labs) <- c("north", "central", "east") # original

soiltype.labs <- c("Heavy soil", "Medium soil", "Light soil") # new
names(soiltype.labs) <- c("heavy", "medium", "light") # original
```


Specify the plot annotations. These will show the **numbers of spring crops** in each rotation.
```{r annotations-scatter-worstcase-oc}
anno_den <- data.frame(
  x = c("HD-HR","HD-HR","HD-HR",
        "HD-HR","HD-HR","HD-HR",
        "HD-HR","HD-HR","HD-HR",
        "LD-HR","LD-HR","LD-HR",
        "LD-HR","LD-HR","LD-HR",
        "LD-HR","LD-HR","LD-HR",
        "LD-LR","LD-LR","LD-LR",
        "LD-LR","LD-LR","LD-LR",
        "LD-LR","LD-LR","LD-LR"
        ),
  y = c(-0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1,
        -0.1,-0.1,-0.1
        ),
  # numbers of spring crops:
  lab = c("3", "3", "3", # north, HD-HR
          "3", "3", "3", # central, HD-HR
          "4", "4", "4", # east, HD-HR
          
          "2", "2", "2", # north, LD-HR
          "2", "2", "2", # central, LD-HR
          "1", "1", "1", # east, LD-HR
          
          "1", "1", "1", # north, LD-LR
          "1", "1", "1", # central, LD-LR
          "0", "0", "0"  # east, LD-LR
          ),
  region = c("north",   "north",   "north", 
             "central", "central", "central",
             "east",    "east",    "east",
             "north",   "north",   "north", 
             "central", "central", "central",
             "east",    "east",    "east",
             "north",   "north",   "north", 
             "central", "central", "central",
             "east",    "east",    "east"
             ),
  soiltype = c("heavy", "medium", "light",
               "heavy", "medium", "light",
               "heavy", "medium", "light",
               "heavy", "medium", "light",
               "heavy", "medium", "light",
               "heavy", "medium", "light",
               "heavy", "medium", "light",
               "heavy", "medium", "light",
               "heavy", "medium", "light"
               ),
  scenario = c("MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT",
               "MIT", "MIT", "MIT"
                )
           ) %>% 
  dplyr::mutate(
    region = factor(region,
                    levels = c("north", "central", "east")
                    ),
    soiltype = factor(soiltype,
                    levels = c("heavy", "medium", "light")
                    )
  )
```

Specify plot.
```{r plot-sp1}
sp1 <- ggplot(density_3dr %>% dplyr::filter(year == 6 & !scenario=="CWW"), #Keep only yr 6, remove CWW
       aes(initDR3, hvh_mean, colour = scenario, shape = scenario)) + 
  facet_grid(region ~ soiltype, labeller = labeller(region = region.labs, 
                                                    soiltype = soiltype.labs)) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylim(-0.15, 1) +
  labs(x = "Initial density and resistance of Black-grass population", 
       y = "Proportion of field with economically- \ndamaging Black-grass density at year 6") +
  # specify colours and shapes for 'scenario':
  scale_color_manual(name = "Scenario",
                     values = c("#00306F", # BAU, madison blue
                                "#00C2F9")) + # MIT, capri blue
  scale_shape_manual(name = "Scenario",
                     values=c(15, 16)) + # BAU 15 = square; MIT 16 = circle
  theme(strip.placement = 'outside',
        strip.text.x = element_text(size = 16),#, color = "red", face = "bold.italic"
        strip.text.y = element_text(size = 16),
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(size=rel(1.7)),
        axis.text.y=element_text(size=rel(1.7)),
        legend.title=element_text(size=18),
        legend.text=element_text(size=16)
  ) +
  geom_pointrange(aes(ymin = hvh_ci_l, 
                      ymax = hvh_ci_u),
                  size = 0.9) + 
  geom_text(data = anno_den, aes(x = x,  y = y, label = lab),
           colour = "grey") 

sp1
```


###        To the above plot I need to add the LD-HR scenario run with initial high density.
For fields with high initial density, I want to see whether black-grass density is reduced by the LD-HR strategies. In these fields, the HD-HR strategies did successfully reduce BG density, but would LD-HR strategies also be successful?

**Add LD-HR run with init high density, and run with initial very high density, to this plot**
```{r, eval=FALSE, echo=FALSE}
sp2 <- ggplot(density_3dr %>% dplyr::filter(year == 6 & !scenario=="CWW"), #Keep only yr 6, remove CWW
       aes(initDR3, hvh_mean, colour = scenario, shape = scenario)) + 
  facet_grid(region ~ soiltype, labeller = labeller(region = region.labs, 
                                                    soiltype = soiltype.labs)) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  ylim(-0.15, 1) +
  labs(x = "Initial density and resistance of Black-grass population", 
       y = "Proportion of field with economically- \ndamaging Black-grass density at year 6") +
  # specify colours and shapes for 'scenario':
  scale_color_manual(name = "Scenario",
                     values = c("#00306F", # BAU, madison blue
                                "#00C2F9")) + # MIT, capri blue
  scale_shape_manual(name = "Scenario",
                     values=c(15, 16)) + # BAU 15 = square; MIT 16 = circle
  theme(strip.placement = 'outside',
        strip.text.x = element_text(size = 16),#, color = "red", face = "bold.italic"
        strip.text.y = element_text(size = 16),
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(size=rel(1.7)),
        axis.text.y=element_text(size=rel(1.7)),
        legend.title=element_text(size=18),
        legend.text=element_text(size=16)
  ) +
  geom_pointrange(aes(ymin = hvh_ci_l, 
                      ymax = hvh_ci_u),
                  size = 0.9) + 
  geom_text(data = anno_den, aes(x = x,  y = y, label = lab),
           colour = "grey") +
  geom_pointrange(data = density_3dr_hd %>% 
                  dplyr::filter(year == 6 & initDR3=="LD-HR" & scenario=="MIT") %>% 
                  dplyr::mutate(
                    initDR3 = recode_factor(initDR3, "LD-HR" = "HD-HR")),
                    #initDR3 = recode_factor(initDR3, "LD-HR" = "HR-HD")),
                  aes(ymin = hvh_ci_l, 
                      ymax = hvh_ci_u),
                  color = "red",
                  #position=position_dodge(width=0.3),
                  size = 0.9,
                  show.legend = FALSE)

sp2
```


