---
title: "Estimate weighted gross profit and summarise"
author: "Alexa Varah"
date: "2023-01-09"
output: html_document
---

# 1. Intro / rationale

This script manipulates ECOMOD output files to create data frames that can be used for analysis. I calculate the weighted gross profit for a field. This is done by weighting by the proportion of squares in each density state.  

**NB** somewhere I need to give details of the proxy crops Rob G used when running his simulations.


# 2. Load packages
```{r load-packages}
rm(list=ls())
library(tidyverse) # for easy data manipulation; includes dplyr, ggplot & more
library(gmodels) # to calculate 95% CIs
```


# 3. Load and tidy data
## 3.1. Load & prep ECOMOD data
### 3.1.1. MIT
```{r load-and-prep-MIT}
## 1. MIT - Create long-format data frames.

## MIT - Low density model run
mit_low <- read.csv("../output/mit_ECOMOD_output_L_combined.csv", header=TRUE) %>% 
  dplyr::select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

mit_low <- reshape(mit_low, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run


## MIT - Medium density model run
mit_med <- read.csv("../output/mit_ECOMOD_output_M_combined.csv", header=TRUE) %>% 
  dplyr::select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

mit_med <- reshape(mit_med, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run


## MIT - High density model run
mit_high <- read.csv("../output/mit_ECOMOD_output_H_combined.csv", header=TRUE) %>% 
  dplyr::select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

mit_high <- reshape(mit_high, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run


## MIT - Very high density model run
mit_vhig <- read.csv("../output/mit_ECOMOD_output_V_combined.csv", header=TRUE) %>% 
  dplyr::select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

mit_vhig <- reshape(mit_vhig, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run


## 2. MIT - Join data frames.
mit_economicdata <- rbind(mit_low, mit_med, mit_high, mit_vhig)

rm(mit_low)
rm(mit_med)
rm(mit_high)
rm(mit_vhig)

# Need to create initcondit col in the same format as in the sim data.
# Also need to add a column that is identical in 
# both the economic and simulation data frames, 
# and which identifies scenario, initial conditions and year.

mit_econdata <- mit_economicdata %>% 
  dplyr::mutate(
    field_name = gsub('\\.', '_', field_name), # replace . with _
    initdenres = sub('_.*', '', field_name), # extract chrs before first '_'
    soiltype = sub('.*\\_', '', field_name), # extract chrs after last '_'
    region = substr(field_name, start = 7, stop = 7), # extract 7th character
    region = tolower(region),
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "ff",
    esID = paste(scenario, initcondit, rotation, sep = "_")
    )

rm(mit_economicdata)
```

### 3.1.2. BAU
```{r load-and-prep-BAU}

## 1. BAU - Create long-format data frames.

## BAU - Low density model run
bau_low <- read.csv("../output/bau_ECOMOD_output_L.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

bau_low <- reshape(bau_low, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run


## BAU - Medium density model run
bau_med <- read.csv("../output/bau_ECOMOD_output_M.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

bau_med <- reshape(bau_med, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run


## BAU - High density model run
bau_high <- read.csv("../output/bau_ECOMOD_output_H.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

bau_high <- reshape(bau_high, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run


## BAU - Very high density model run
bau_vhig <- read.csv("../output/bau_ECOMOD_output_V.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

bau_vhig <- reshape(bau_vhig, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run


## 2. BAU - Join data frames.
bau_economicdata <- rbind(bau_low, bau_med, bau_high, bau_vhig)

rm(bau_low)
rm(bau_med)
rm(bau_high)
rm(bau_vhig)

# Need to create initcondit col in the same format as in the sim data.
# Also need to add a column that is identical in 
# both the economic and simulation data frames, 
# and which identifies scenario, initial conditions and year.

bau_econdata <- bau_economicdata %>% 
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
    
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),

    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "bau",
    esID = paste(scenario, initcondit, rotation, sep = "_")
  )

rm(bau_economicdata)
```


### 3.1.3. CWW
```{r}
## 1. CWW - Create long-format data frames.

## CWW - Low density model run
cww_low <- read.csv("../output/cww_ECOMOD_output_L.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

cww_low <- reshape(cww_low, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run


## CWW - Medium density model run
cww_med <- read.csv("../output/cww_ECOMOD_output_M.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

cww_med <- reshape(cww_med, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run


## CWW - High density model run
cww_high <- read.csv("../output/cww_ECOMOD_output_H.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

cww_high <- reshape(cww_high, varying=c(2:85), direction="long", 
                    idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run


## CWW - Very high density model run
cww_vhig <- read.csv("../output/cww_ECOMOD_output_V.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

cww_vhig <- reshape(cww_vhig, varying=c(2:85), direction="long", 
                    idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run


## 2. CWW - Join data frames.
cww_economicdata <- rbind(cww_low, cww_med, cww_high, cww_vhig)

rm(cww_low)
rm(cww_med)
rm(cww_high)
rm(cww_vhig)

# Need to create initcondit col in the same format as in the sim data.
# Also need to add a column that is identical in 
# both the economic and simulation data frames, 
# and which identifies scenario, initial conditions and year.

cww_econdata <- cww_economicdata %>% 
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
    
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),
    
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "cww",
    esID = paste(scenario, initcondit, rotation, sep = "_")
  )

rm(cww_economicdata)
```



### 3.1.4. Join all economic scenarios & tidy
```{r}
econdata <- rbind(mit_econdata, bau_econdata, cww_econdata) %>% 
  dplyr::select(-field_name)

# change lower-case scenario to upper-case, and change FF to MIT.
econdata <- econdata %>% 
  dplyr::mutate(scenario = toupper(scenario),
                scenario = str_replace_all(scenario, "FF","MIT"),
                esID = str_replace_all(esID, "ff","MIT"),
                esID = str_replace_all(esID, "bau","BAU"),
                esID = str_replace_all(esID, "cww","CWW")
                ) 

## Clean up
rm(mit_econdata)
rm(bau_econdata)
rm(cww_econdata)
```

## 3.2. Load simulated density data
Load the tidied simulation data. Combine the 'a' and 'l' columns as I don't differentiate between black-grass being absent and being low density in ECOMOD. Add a column that is identical in both the economic and simulation data frames, and which identifies scenario, initial conditions and year.
```{r load-density-data}
simdata <- readRDS(file = "../output/simulation_results_tidy.rds") %>%
  # sum the proportions of absent and low density black-grass
  rowwise() %>% 
  dplyr::mutate(al = sum(c_across(a:l), na.rm = T)) %>% # new category: absent & low
  ungroup() %>% 
  # new ID on which to join this data frame with the economic data
  dplyr::mutate(esID = paste(scenario, initcondit, year, sep="_"))  

simdata_hd <- readRDS(file = "../output/simulation_results_tidy_hd.rds") %>%
  # sum the proportions of absent and low density black-grass
  rowwise() %>% 
  dplyr::mutate(al = sum(c_across(a:l), na.rm = T)) %>% # new category: absent & low
  ungroup() %>% 
  # new ID on which to join this data frame with the economic data
  dplyr::mutate(esID = paste(scenario, initcondit, year, sep="_"))  
```


# 4. Calculate weighted values

To do this, join the simulated density-resistance data and the economic data.

Only winter wheat yield will vary depending on black-grass density; yield of all other crops will be unaffected by the weighting process. I calculate weighted yield, output, fuel cost, labour cost and operations cost. Fuel, labour and operations costs (in ECOMOD, Operation cost = Fuel cost + Labour cost) all involve using work rates in their calculation. Work rate is a function of crop yield and so these variables  will be affected by black-grass density when the crop is wheat. When you do the join, the `econdata` rows will automatically repeat to fill the 37 iterations present in `simdata`.  

Not all variables need to be weighted as they are not all affected by crop yield and will therefore not respond to changes in BG density. Furthermore, even weighted variables won't always show differences between imputations as at low and medium densities, black-grass doesn't affect yield.  
  
Opportunity cost is calculated as CWW-BAU or MIT-BAU. This means that negative values indicate BAU had higher gross profit, so the other scenario makes the farmer less money.

```{r calculate-weighted-values}
weighted_df <- left_join(simdata, econdata, by="esID") %>% 
  # Calculate weighted gross profit for each row for the affected variables
  dplyr::mutate(
    wtd_gp = case_when(
      modelrun == "low" ~ al*grossprof,
      modelrun == "medium" ~ m*grossprof,
      modelrun == "high" ~ h*grossprof,
      modelrun == "veryhigh" ~ v*grossprof
    ),
    wtd_fuelcost = case_when(
      modelrun == "low" ~ al*fuelcost,
      modelrun == "medium" ~ m*fuelcost,
      modelrun == "high" ~ h*fuelcost,
      modelrun == "veryhigh" ~ v*fuelcost
    ),
    wtd_labcost = case_when(
      modelrun == "low" ~ al*labcost,
      modelrun == "medium" ~ m*labcost,
      modelrun == "high" ~ h*labcost,
      modelrun == "veryhigh" ~ v*labcost
    ),
    wtd_opscost = case_when(
      modelrun == "low" ~ al*opcost,
      modelrun == "medium" ~ m*opcost,
      modelrun == "high" ~ h*opcost,
      modelrun == "veryhigh" ~ v*opcost
    ),
    wtd_yield = case_when(
      modelrun == "low" ~ al*yield,
      modelrun == "medium" ~ m*yield,
      modelrun == "high" ~ h*yield,
      modelrun == "veryhigh" ~ v*yield
    ),
    wtd_output = case_when(
      modelrun == "low" ~ al*output,
      modelrun == "medium" ~ m*output,
      modelrun == "high" ~ h*output,
      modelrun == "veryhigh" ~ v*output
    )
  ) %>%
  # Add weighted variables across model runs (low, med, high & vhigh den) 
  # to get total gross profit, yield etc (i.e. add the contributions from the 
  # different densities in different parts of the field) for each year of each 
  # strategy (ID), and for each imputation of that year-strategy (imp).
  dplyr::group_by(imp, esID) %>% 
  dplyr::summarise(
    wtd_gp = sum(wtd_gp),
    wtd_fuelcost = sum(wtd_fuelcost),
    wtd_labcost = sum(wtd_labcost),
    wtd_opscost = sum(wtd_opscost),
    wtd_yield = sum(wtd_yield),
    wtd_output = sum(wtd_output)
  ) %>% 
  # create columns for scenario, region, soil type, init condits, year
  separate(esID, into=c("scenario","region","soiltype","initdenres","year"), sep="_") %>% 
  dplyr::mutate( 
    scenario = factor(scenario),
    region = factor(region),
    soiltype = factor(soiltype),
    year = as.integer(year),
    # create column of initial conditions
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    # re-name levels of region and soiltype, then re-order levels
    region = forcats::fct_recode(region,
                                 "north" = "n", # new, old
                                 "central" = "c",
                                 "east" = "e"),
    region = factor(region, levels=c("north", "central", "east")),
    soiltype = forcats::fct_recode(soiltype,
                                   "heavy" = "h", # new, old
                                   "medium" = "m",
                                   "light" = "l"),
    soiltype = factor(soiltype, levels=c("heavy", "medium", "light")),
    initdenres = factor(initdenres, # specify order of levels
                        levels = c("VD-HR", "HD-HR", "MD-HR", 
                                   "MD-LR", "LD-HR", "LD-LR")),
    # specify order of levels so later plots are in correct order:
    initcondit = factor(initcondit, levels = c(
      "n_h_VD-HR", "n_m_VD-HR", "n_l_VD-HR", 
      "c_h_VD-HR", "c_m_VD-HR", "c_l_VD-HR",
      "e_h_VD-HR", "e_m_VD-HR", "e_l_VD-HR",
      
      "n_h_HD-HR", "n_m_HD-HR", "n_l_HD-HR",
      "c_h_HD-HR", "c_m_HD-HR", "c_l_HD-HR",
      "e_h_HD-HR", "e_m_HD-HR", "e_l_HD-HR",
      
      "n_h_MD-HR", "n_m_MD-HR", "n_l_MD-HR",
      "c_h_MD-HR", "c_m_MD-HR", "c_l_MD-HR",
      "e_h_MD-HR", "e_m_MD-HR", "e_l_MD-HR",
      
      "n_h_MD-LR", "n_m_MD-LR", "n_l_MD-LR",
      "c_h_MD-LR", "c_m_MD-LR", "c_l_MD-LR",
      "e_h_MD-LR", "e_m_MD-LR", "e_l_MD-LR",
      
      "n_h_LD-HR", "n_m_LD-HR", "n_l_LD-HR",
      "c_h_LD-HR", "c_m_LD-HR", "c_l_LD-HR",
      "e_h_LD-HR", "e_m_LD-HR", "e_l_LD-HR",
      
      "n_h_LD-LR", "n_m_LD-LR", "n_l_LD-LR",
      "c_h_LD-LR", "c_m_LD-LR", "c_l_LD-LR",
      "e_h_LD-LR", "e_m_LD-LR", "e_l_LD-LR")),

    esID = paste(scenario, substr(region, 1, 1), substr(soiltype, 1, 1), 
                 initdenres, year, sep = "_")
  ) %>% 
  # calculate opportunity cost of switching out of BAU
  group_by(imp, initcondit, year) %>% 
  dplyr::mutate(wtd_opp_cost = wtd_gp - wtd_gp[scenario == "BAU"]) %>% 
  ungroup() %>% 
  arrange(scenario, initcondit, year)


# Join other variables back on:

# First, select just the variables I want.
econdata_small <- econdata %>% 
  dplyr::select(esID, crop, fertcost, seedcost, herbcost, sundry, varcost) %>% 
  distinct(esID, .keep_all=TRUE)

# Then join back on.
econ_allimp <- inner_join(econdata_small, weighted_df,  by = "esID") %>% 
  dplyr::relocate(
    imp, esID, scenario, region, soiltype, initdenres, initcondit, year, crop,
    wtd_yield, wtd_gp, wtd_output, wtd_fuelcost, wtd_labcost, wtd_opscost) %>% 
  rename(ID = esID) %>% 
  arrange(scenario, initdenres, region, soiltype)

# Clean up
rm(econdata_small)
rm(weighted_df)
```

Save output file.
```{r}
write.csv(econ_allimp,"../output/economic_data_for_analysis-all_imputations.csv", row.names = FALSE)
```



# 5. Re-do it for LD-HR strategies on HD-HR fields

To do this, join the simulated density-resistance data and the economic data.

Only winter wheat yield will vary depending on black-grass density; yield of all other crops will be unaffected by the weighting process. I calculate weighted yield, fuel cost, labour cost and operations cost. Fuel, labour and operations costs all involve using work rates in their calculation. Work rate is a function of crop yield and so these variables  will be affected by black-grass density when the crop is wheat. When you do the join, the `econdata` rows will automatically repeat to fill the 37 iterations present in `simdata`.  

Not all variables need to be weighted as they are not all affected by crop yield and will therefore not respond to changes in BG density. Furthermore, even weighted variables won't always show differences between imputations as at low and medium densities, Black-grass doesn't affect yield.  
  
Opportunity cost is calculated as CWW-BAU or MIT-BAU. This means that negative values indicate BAU had higher gross profit, so the other scenario makes the farmer less money.

```{r calculate-weighted-values-hd}
weighted_df_hd <- left_join(simdata_hd, econdata, by="esID") %>% 
  # Calculate weighted gross profit for each row for the affected variables
  dplyr::mutate(
    wtd_gp = case_when(
      modelrun == "low" ~ al*grossprof,
      modelrun == "medium" ~ m*grossprof,
      modelrun == "high" ~ h*grossprof,
      modelrun == "veryhigh" ~ v*grossprof
    ),
    wtd_fuelcost = case_when(
      modelrun == "low" ~ al*fuelcost,
      modelrun == "medium" ~ m*fuelcost,
      modelrun == "high" ~ h*fuelcost,
      modelrun == "veryhigh" ~ v*fuelcost
    ),
    wtd_labcost = case_when(
      modelrun == "low" ~ al*labcost,
      modelrun == "medium" ~ m*labcost,
      modelrun == "high" ~ h*labcost,
      modelrun == "veryhigh" ~ v*labcost
    ),
    wtd_opscost = case_when(
      modelrun == "low" ~ al*opcost,
      modelrun == "medium" ~ m*opcost,
      modelrun == "high" ~ h*opcost,
      modelrun == "veryhigh" ~ v*opcost
    ),
    wtd_yield = case_when(
      modelrun == "low" ~ al*yield,
      modelrun == "medium" ~ m*yield,
      modelrun == "high" ~ h*yield,
      modelrun == "veryhigh" ~ v*yield
    ),
    wtd_output = case_when(
      modelrun == "low" ~ al*output,
      modelrun == "medium" ~ m*output,
      modelrun == "high" ~ h*output,
      modelrun == "veryhigh" ~ v*output
    )
  ) %>%
  # Add weighted variables across model runs (low, med, high & vhigh den) 
  # to get total gross profit, yield etc (i.e. add the contributions from the 
  # different densities in different parts of the field) for each year of each 
  # strategy (ID), and for each imputation of that year-strategy (imp).
  dplyr::group_by(imp, esID) %>% 
  dplyr::summarise(
    wtd_gp = sum(wtd_gp),
    wtd_fuelcost = sum(wtd_fuelcost),
    wtd_labcost = sum(wtd_labcost),
    wtd_opscost = sum(wtd_opscost),
    wtd_yield = sum(wtd_yield),
    wtd_output = sum(wtd_output)
  ) %>% 
  # create columns for scenario, region, soil type, init condits, year
  separate(esID, into=c("scenario","region","soiltype","initdenres","year"), sep="_") %>% 
  dplyr::mutate( 
    scenario = factor(scenario),
    region = factor(region),
    soiltype = factor(soiltype),
    year = as.integer(year),
    # create column of initial conditions
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    # re-name levels of region and soiltype, then re-order levels
    region = forcats::fct_recode(region,
                                 "north" = "n", # new, old
                                 "central" = "c",
                                 "east" = "e"),
    region = factor(region, levels=c("north", "central", "east")),
    soiltype = forcats::fct_recode(soiltype,
                                   "heavy" = "h", # new, old
                                   "medium" = "m",
                                   "light" = "l"),
    soiltype = factor(soiltype, levels=c("heavy", "medium", "light")),
    initdenres = factor(initdenres, # specify order of levels
                        levels = c("VD-HR", "HD-HR", "MD-HR", 
                                   "MD-LR", "LD-HR", "LD-LR")),
    # specify order of levels so later plots are in correct order:
    initcondit = factor(initcondit, levels = c(
      "n_h_VD-HR", "n_m_VD-HR", "n_l_VD-HR", 
      "c_h_VD-HR", "c_m_VD-HR", "c_l_VD-HR",
      "e_h_VD-HR", "e_m_VD-HR", "e_l_VD-HR",
      
      "n_h_HD-HR", "n_m_HD-HR", "n_l_HD-HR",
      "c_h_HD-HR", "c_m_HD-HR", "c_l_HD-HR",
      "e_h_HD-HR", "e_m_HD-HR", "e_l_HD-HR",
      
      "n_h_MD-HR", "n_m_MD-HR", "n_l_MD-HR",
      "c_h_MD-HR", "c_m_MD-HR", "c_l_MD-HR",
      "e_h_MD-HR", "e_m_MD-HR", "e_l_MD-HR",
      
      "n_h_MD-LR", "n_m_MD-LR", "n_l_MD-LR",
      "c_h_MD-LR", "c_m_MD-LR", "c_l_MD-LR",
      "e_h_MD-LR", "e_m_MD-LR", "e_l_MD-LR",
      
      "n_h_LD-HR", "n_m_LD-HR", "n_l_LD-HR",
      "c_h_LD-HR", "c_m_LD-HR", "c_l_LD-HR",
      "e_h_LD-HR", "e_m_LD-HR", "e_l_LD-HR",
      
      "n_h_LD-LR", "n_m_LD-LR", "n_l_LD-LR",
      "c_h_LD-LR", "c_m_LD-LR", "c_l_LD-LR",
      "e_h_LD-LR", "e_m_LD-LR", "e_l_LD-LR")),

    esID = paste(scenario, substr(region, 1, 1), substr(soiltype, 1, 1), 
                 initdenres, year, sep = "_")
  ) %>% 
  # calculate opportunity cost of switching out of BAU
  group_by(imp, initcondit, year) %>% 
  dplyr::mutate(wtd_opp_cost = wtd_gp - wtd_gp[scenario == "BAU"]) %>% 
  ungroup() %>% 
  arrange(scenario, initcondit, year)


# Join other variables back on:

# First, select just the variables I want.
econdata_small <- econdata %>% 
  dplyr::select(esID, crop, fertcost, seedcost, herbcost, sundry, varcost) %>% 
  distinct(esID, .keep_all=TRUE)

# Then join back on.
econ_allimp_hd <- inner_join(econdata_small, weighted_df_hd,  by = "esID") %>% 
  dplyr::relocate(imp, esID, scenario, region, soiltype, initdenres, initcondit, year, crop,
           wtd_yield, wtd_gp, wtd_output, wtd_fuelcost, wtd_labcost, wtd_opscost) %>% 
  rename(ID = esID) %>% 
  arrange(scenario, initdenres, region, soiltype)

# Clean up
rm(econdata_small)
rm(weighted_df_hd)
```

Save output file.
```{r}
write.csv(econ_allimp_hd,"../output/economic_data_for_analysis-all_imputations_hd.csv", row.names = FALSE)
```



# Session info
```{r}
#packageVersion('gmodels')
```

