---
title: "Gross profit analysis - summary stats and plots"
author: "Alexa Varah"
date: "15/02/2022"
output: html_document
---

# 1. Intro
This script looks at what happens to gross profit under different scenarios and initial conditions.  

Definitions of the variables used here:  
  
* **imp** = density estimation imputation (there were 37 (previously 97) imputations for each year of each rotation).    
* **scenario** = three potential future farm management scenarios: Business As Usual (BAU), Continuous Winter Wheat (CWW) or Mitigation of herbicide-resistant black-grass populations (MIT).  
* **region** = north, central and east. These were the regions we asked farmers to tailor their MIT strategies to.  
* **soiltype** = broad categorisation of soils into heavy/medium or light. These were the soil types we asked farmers to tailor their MIT strategies to.  
* **initdenres** = initial density and resistance status of a theoretical field. These were the density and resistance states we asked farmers to tailor their MIT strategies to. L = low; H = high; D = density; R = resistance.  
* **yr** = year of rotation (all rotations were 6 years).  
* **wtd_gp** = weighted gross profit. Gross profit weighted as for yield.  
  
# 2. Set up

## 2.1. Load packages & functions
```{r load-packages, message=FALSE}
rm(list=ls())
library(tidyverse)
#library(patchwork) # for panel plots
```

Load function to count complete observations
```{r}
nobs <- function(x) length(x[!is.na(x)])
```

Load function to specify number of decimal places to show.
```{r}
# k is the number and d is the number of decimals to show. 
# trimws removes any leading white space which can be useful if you have a vector of numbers.
specify_decimal <- function(k, d) trimws(format(round(k, d), nsmall=d))
# USE:
#specify_decimal(mean(x),2)
```

## 2.2. Load data
```{r load-data}
econ_3DR <- read.csv("../output/economic_data_for_analysis_3DR.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))

econ_3DR_hd <- read.csv("../output/economic_data_for_analysis_3DR_hd.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))

#econ_6DR <- read.csv("../output/economic_data_for_analysis_6DR.csv", header = T) %>% 
#  dplyr::mutate(
#    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
#    region = factor(region, levels = c("north", "central", "east")),
#    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
#    initdenres = factor(initdenres, 
#                        levels = c(
#                          "LD-LR", "MD-LR",
#                          "LD-HR", "MD-HR",
#                          "HD-HR", "VD-HR" 
#                          )))

econ_allimp <- read.csv("../output/economic_data_for_analysis-all_imputations.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres, 
                        levels = c(
                          "LD-LR", "MD-LR",
                          "LD-HR", "MD-HR",
                          "HD-HR", "VD-HR" 
                          )))

econ_allimp_hd <- read.csv("../output/economic_data_for_analysis-all_imputations_hd.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres, 
                        levels = c(
                          "LD-LR", "MD-LR",
                          "LD-HR", "MD-HR",
                          "HD-HR", "VD-HR" 
                          )))
```

# 3. Summary stats for paper

When calculating mean rotation gross profit, I average across imputations (this is already done - resulting file is `econ3DR`) before averaging across rotations. The order in which we do the averaging will affect what information is contained in the standard deviation. If you do it the other way round (find mean rotation gross profit THEN average this across imputations), the SD will be that of the imputations (tiny) rather than giving an idea of how gross profit varies throughout the rotation (bigger). By averaging across imputations first, and then finding the rotation mean, the SD will tell us how gross profit varies through the rotation. 

## 3.1. Mean annual (across a rotation) gross profit by scenario

Calculate mean annual gross profit first and then summarize across regions, soil types and initial den-res categories. This will give variation due to region, soil type and initial den-res rather than the CI also including year-to-year variation.
```{r}
econ_3DR %>% 
  # find rotation mean first
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    gp_mean = mean(wtd_gp_mean, na.rm = TRUE),
    gp_ci_l = mean(wtd_gp_mean, na.rm = TRUE) - 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(length(wtd_gp_mean))),
    gp_ci_u = mean(wtd_gp_mean, na.rm = TRUE) + 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(length(wtd_gp_mean)))
    ) %>% 
  #ungroup() %>% # makes no difference here whether this line is run or not
  # then find scenario mean
  dplyr::group_by(scenario) %>% 
  dplyr::summarize(
    gp = mean(gp_mean, na.rm = TRUE),
    gp_cil = mean(gp_mean, na.rm = TRUE) - 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean))),
    gp_ciu = mean(gp_mean, na.rm = TRUE) + 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean)))
    )
```



## 3.2. Mean annual (across a rotation) gross profit by scenario and init den-res
```{r}
econ_3DR %>% 
  # find rotation mean first
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    gp_mean = mean(wtd_gp_mean, na.rm = TRUE),
    gp_ci_l = mean(wtd_gp_mean, na.rm = TRUE) - 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(length(wtd_gp_mean))),
    gp_ci_u = mean(wtd_gp_mean, na.rm = TRUE) + 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(length(wtd_gp_mean)))
    ) %>% 
  # then find scenario mean
  dplyr::group_by(scenario, initdenres_collapsed) %>% 
  dplyr::summarize(
    gp = mean(gp_mean, na.rm = TRUE),
    gp_ci_l = mean(gp_mean, na.rm = TRUE) - 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean))),
    gp_ci_u = mean(gp_mean, na.rm = TRUE) + 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean)))
    )
```



## 3.3. Difference in gross profit (opportunity cost) between MIT and BAU, 3 denres

### For each denres level
```{r}
econ_3DR %>% 
  # find rotation mean
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    gp_mean = mean(wtd_gp_mean, na.rm = TRUE),
    gp_ci_l = mean(wtd_gp_mean, na.rm = TRUE) - 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(nobs(wtd_gp_mean))),
    gp_ci_u = mean(wtd_gp_mean, na.rm = TRUE) + 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(nobs(wtd_gp_mean))),
    oc_mean = mean(wtd_opp_cost_mean, na.rm = TRUE),
    oc_ci_l = mean(wtd_opp_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(wtd_opp_cost_mean, na.rm = TRUE) / sqrt(nobs(wtd_opp_cost_mean))),
    oc_ci_u = mean(wtd_opp_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(wtd_opp_cost_mean, na.rm = TRUE) / sqrt(nobs(wtd_opp_cost_mean)))
    ) %>% 
  # find regional mean
  dplyr::group_by(scenario, initdenres_collapsed) %>% 
  dplyr::summarize(
    gp = mean(gp_mean, na.rm = TRUE),
    gp_ci_l = mean(gp_mean, na.rm = TRUE) - 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean))),
    gp_ci_u = mean(gp_mean, na.rm = TRUE) + 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean))),
    oc = mean(oc_mean*(-1), na.rm = TRUE),
    oc_ci_l = mean(oc_mean*(-1), na.rm = TRUE) - 
      (1.96 * sd(oc_mean*(-1), na.rm = TRUE) / sqrt(length(oc_mean*(-1)))),
    oc_ci_u = mean(oc_mean*(-1), na.rm = TRUE) + 
      (1.96 * sd(oc_mean*(-1), na.rm = TRUE) / sqrt(length(oc_mean*(-1))))
    ) %>% 
  dplyr::filter(scenario=="MIT")
```

For the opportunity costs, a negative value indicates that MIT wins.  
95% CIs show the variation due to region and soil type.  

### What are the opportunity costs (of switching to MIT) by region and initdenres category
Find mean annual opportunity costs first, THEN average across soil types. This will mean that the CIs reflect variation due to regional differences, rather than also including year-to-year variation. 
```{r}
econ_3DR %>% 
  # find rotation mean
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    gp_mean = mean(wtd_gp_mean, na.rm = TRUE),
    gp_ci_l = mean(wtd_gp_mean, na.rm = TRUE) - 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(nobs(wtd_gp_mean))),
    gp_ci_u = mean(wtd_gp_mean, na.rm = TRUE) + 
      (1.96 * sd(wtd_gp_mean, na.rm = TRUE) / sqrt(nobs(wtd_gp_mean))),
    oc_mean = mean(wtd_opp_cost_mean, na.rm = TRUE),
    oc_ci_l = mean(wtd_opp_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(wtd_opp_cost_mean, na.rm = TRUE) / sqrt(nobs(wtd_opp_cost_mean))),
    oc_ci_u = mean(wtd_opp_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(wtd_opp_cost_mean, na.rm = TRUE) / sqrt(nobs(wtd_opp_cost_mean)))
    ) %>% 
  # find regional mean
  dplyr::group_by(scenario, region, initdenres_collapsed) %>% 
  dplyr::summarize(
    gp = mean(gp_mean, na.rm = TRUE),
    gp_ci_l = mean(gp_mean, na.rm = TRUE) - 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean))),
    gp_ci_u = mean(gp_mean, na.rm = TRUE) + 
      (1.96 * sd(gp_mean, na.rm = TRUE) / sqrt(length(gp_mean))),
    oc = mean(oc_mean*(-1), na.rm = TRUE),
    oc_ci_l = mean(oc_mean*(-1), na.rm = TRUE) - 
      (1.96 * sd(oc_mean*(-1), na.rm = TRUE) / sqrt(length(oc_mean*(-1)))),
    oc_ci_u = mean(oc_mean*(-1), na.rm = TRUE) + 
      (1.96 * sd(oc_mean*(-1), na.rm = TRUE) / sqrt(length(oc_mean*(-1))))
    ) %>% 
  dplyr::filter(scenario=="MIT")
```

For the opportunity costs, a negative value indicates that MIT wins.  
95% CIs reflect variation due to region.  




# 4. Create data frames for plots
## 4.1. Line graph - annual gross profit by scenario & initdenres (3 denres levels)

#### Create data frame
```{r}
df1 <- econ_3DR %>% 
  group_by(scenario, year, initdenres_collapsed) %>% # grouping factor for sum
  dplyr::mutate(
    # gross profit           
    gp = mean(wtd_gp_mean),
    gp_ci_l = gp - (1.96 * (sd(wtd_gp_mean) / sqrt(length(wtd_gp_mean)))),
    gp_ci_u = gp + (1.96 * (sd(wtd_gp_mean) / sqrt(length(wtd_gp_mean)))),
    # opportunity cost
    oc = mean(wtd_opp_cost_mean),
    oc_ci_l = oc - 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean)))),
    oc_ci_u = oc + 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, year, initdenres_collapsed, .keep_all = TRUE) %>% 
  dplyr::select(scenario, year, initdenres_collapsed, gp:oc_ci_u) %>% 
  dplyr::mutate(scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")))
```


##### Save data frame
Save data frame as it's used in the 'Plots' script.

```{r}
write.csv(df1, "../output/data for line graph_gross profit.csv", 
          row.names = FALSE)
```



## 4.2. Scatter plot - rotation gross profit, 3 denres

### Create data frame for plot
```{r}
df2 <- econ_3DR %>% 
  group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::mutate(
    # gross profit           
    gp = mean(wtd_gp_mean),
    gp_ci_l = gp - (1.96 * (sd(wtd_gp_mean) / sqrt(length(wtd_gp_mean)))),
    gp_ci_u = gp + (1.96 * (sd(wtd_gp_mean) / sqrt(length(wtd_gp_mean)))),
    # opportunity cost
    oc = mean(wtd_opp_cost_mean),
    oc_ci_l = oc - 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean)))),
    oc_ci_u = oc + 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, region, soiltype, initdenres_collapsed, .keep_all = TRUE) %>% 
  dplyr::select(scenario, region, soiltype, initdenres_collapsed, gp:oc_ci_u)
```

### Save data 
This is used for a plot in the paper so save as output.
```{r}
write.csv(df2, "../output/data for scatter plot_gross profit.csv",
          row.names = FALSE)
```

## 4.3. Scatter plot - rotation gross profit, 3 denres, NO CWW - add LD-HR run with init HD

### Create data frame for plot
```{r}
df2_hd <- econ_3DR_hd %>% 
  group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::mutate(
    # gross profit           
    gp = mean(wtd_gp_mean),
    gp_ci_l = gp - (1.96 * (sd(wtd_gp_mean) / sqrt(length(wtd_gp_mean)))),
    gp_ci_u = gp + (1.96 * (sd(wtd_gp_mean) / sqrt(length(wtd_gp_mean)))),
    # opportunity cost
    oc = mean(wtd_opp_cost_mean),
    oc_ci_l = oc - 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean)))),
    oc_ci_u = oc + 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, region, soiltype, initdenres_collapsed, .keep_all = TRUE) %>% 
  dplyr::select(scenario, region, soiltype, initdenres_collapsed, gp:oc_ci_u)
```

### Save data 
This is used for a plot in the paper so save as output.
```{r}
write.csv(df2_hd, "../output/data for scatter plot_gross profit_hd.csv",
          row.names = FALSE)
```


# 5. Session info
```{r}
sessionInfo()
```

