---
title: "Gross profit - worst case"
author: "Alexa Varah"
date: "07/03/2022"
output: html_document
---

# 1. Intro
This script explores the extremes. The extreme is continuing doing BAU and eventually driving resistance and density to the point where there is very high density black-grass in all grid cells in a field.

I want to answer the question: As density in a field increases to the worst levels (i.e. very high density everywhere), does it ever become financially viable to be doing MIT strategies? Is there a situation where we should act preemptively?
In other words, is it financially better to switch pre-emptively to MIT, or is it financially better to continue with BAU in the knowledge that weed density will get worse?  
  
To answer this, I look at the opportunity costs of switching out of BAU and into MIT for worst-case (very high density) conditions. Current opportunity costs are *BAU, current density – MIT, current density*, which I calculated in script 04a and are therefore already in `econ_3DR`; worst-case opportunity costs, calculated here, are *BAU, worst-case density – MIT, current density*.

I calculate opportunity costs by doing MIT-BAU. This assumes that the chosen option is BAU. For this plot, I want the chosen option to be MIT, and the foregone option to be BAU. So I just need to reverse the sign on the opportunity costs. 

**Assumptions:** every grid cell in a field is in very high density. This follows on from the worst-case scenario we explored in the previous paper. We don't assert that it is a situation that's ever likely to happen: we're just exploring it as the worst possible case.

I'm not including CWW in this analysis as Rob G and my models show that it's nether financially better than BAU nor does it control Black-grass populations. 

# 2. Set up
## 2.1. Load packages
```{r load-packages, message=FALSE}
rm(list=ls())
library(tidyverse) # for data manipulation; includes dplyr, ggplot2 & more
```

## 2.2. Load functions
This counts complete observations.
```{r}
nobs <- function(x) length(x[!is.na(x)])
```

## 2.3. Load data
I'm only loading the very high model run for the BAU economic data. This is because I am assuming that continuing with BAU strategies has driven ALL grid cells in a field to have very high densities of black-grass. This means there will be no weighting of yield or gross profit as there's no density state distribution within a field.
```{r load-data}
# BAU - ECOMOD very high density model run
bau_vhig <- read.csv("../output/bau_ECOMOD_output_V.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  dplyr::rename_with(stringr::str_replace, 
              # add '.' b4 the number in 'crop' colnames:
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  dplyr::rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# BAU & MIT, current density
econ_3DR <- read.csv("../output/economic_data_for_analysis_3DR.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR"))) %>% 
  dplyr::filter(!scenario == "CWW") %>% 
  droplevels()
```


# 3. Tidy data

Tidy BAU worst case data (i.e. very high model run only). Reshape from wide to long, and create some new columns for soil type, region etc. Also collapse density-resistance levels and calculate mean rotation gross profit.  
```{r BAU-worstcase-reshape-tidy-calc-mean-gp}
bau_worstcase <- bau_vhig %>%
  # reshape
  tidyr::pivot_longer(
    cols = c(2:85),
    names_to = c(".value", "year"),
    names_sep = '\\.'
    ) %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::arrange(field_name) %>% 
  # make columns for soil, region, initial density etc
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
 
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),
    # recode soil type and region, and specify order of factor levels
    soiltype = dplyr::recode(soiltype,
                      "h" = "heavy",
                      "m" = "medium",
                      "l" = "light"),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium", "light")
                      ),
    region = dplyr::recode(region,
                    "n" = "north",
                    "c" = "central",
                    "e" = "east"),
    region = factor(region,
                    levels = c("north", "central", "east")
                    ),
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "BAU"
    ) %>%
  # make it easier to look at
  dplyr::relocate(scenario, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name) %>% 
  # collapse den-res levels
  dplyr::mutate(
    initdenres_collapsed = fct_recode(
      initdenres, 
      "LD-LR" = "MD-LR",# LD-LR & MD-LR (best case)
      "LD-HR" = "MD-HR",# LD-HR & MD-HR (intermediate case) 
      "HD-HR" = "VD-HR"),# HD-HR & VD-HR (worst case)
    initdenres_collapsed = factor(initdenres_collapsed,
      levels = c("LD-LR", "LD-HR", "HD-HR"))
    ) %>% 
  # calculate mean gross profit across the new den-res levels
  group_by(scenario, region, soiltype, year, initdenres_collapsed) %>% 
  dplyr::summarise(mean_gp = mean(grossprof)) %>%
  arrange(scenario, region, soiltype, initdenres_collapsed, year) %>% 
  dplyr::mutate(
    situation="Worst case",
    year = as.integer(year)
    )
```
  


# 4. Create data frame for plot

Create two new data frames, one for each type of opportunity cost (current, worst-case).

## 4.1. Create dataframe of *BAU, current density – MIT, current density* opp costs
From `econ_3DR` I need:  
1. current opportunity costs, which are in the MIT rows (because I did BAU-MIT, so the BAU rows have zeroes in the opportunity costs column)  
2. scenario, region, soiltype, initdenres_collapsed, year  
3. rotation mean opportunity costs.

For point 3, data needs to be averaged over the 6 years to give mean opportunity cost over a rotation.  
The confidence intervals around the rotation mean opportunity costs will reflect the difference between profit obtained from, for example, BAU winter wheat in year 1 and MIT fallow in year 1. So the CIs will be large, as in individual years the opportunity costs may be very large.
```{r}
oppcosts_current <- econ_3DR %>% 
  dplyr::filter(scenario=="MIT") %>% 
  dplyr::select(scenario, region, soiltype, initdenres_collapsed, 
                year, wtd_opp_cost_mean) %>% 
  # calculate rotation mean
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarise(
    oc = mean(wtd_opp_cost_mean, na.rm = TRUE),
    oc_ci_l = mean(wtd_opp_cost_mean, na.rm = TRUE) - 
      (1.96 * (sd(wtd_opp_cost_mean, na.rm = TRUE) / sqrt(nobs(wtd_opp_cost_mean)))),
    oc_ci_u = mean(wtd_opp_cost_mean, na.rm = TRUE) + 
      (1.96 * (sd(wtd_opp_cost_mean, na.rm = TRUE) / sqrt(nobs(wtd_opp_cost_mean))))
    ) %>% 
  arrange(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::mutate(situation="Current") %>% 
  ungroup() %>% 
  dplyr::select(-scenario)
```



## 4.2. Create dataframe of *BAU, worst case – MIT, current density* opp costs

1. Join worst-case BAU gross profit data and current MIT gross profit data.  
2. Calculate the opportunity cost.  
3. Find the rotation mean.  
```{r}
# 1. Extract current MIT gross profit data
mit_current <- econ_3DR %>% 
  dplyr::filter(scenario=="MIT") %>% 
  dplyr::select(scenario, region, soiltype, year, 
                initdenres_collapsed, wtd_gp_mean) %>% 
  dplyr::rename(mean_gp = wtd_gp_mean) %>%
  dplyr::arrange(scenario, region, soiltype, initdenres_collapsed, year) %>% 
  dplyr::mutate(situation="Current") %>% 
  dplyr::mutate(year = as.integer(year))

# 2. Join current MIT data to worst case BAU data, calculate opp cost, calculate rotation mean
oppcosts_worstcase <- rbind(bau_worstcase, mit_current) %>% 
  # calculate opp cost
  dplyr::group_by(region, soiltype, initdenres_collapsed, year) %>% 
  dplyr::mutate(opp_cost = mean_gp - mean_gp[scenario == "BAU"]) %>% 
  # calculate rotation mean
  dplyr::filter(scenario=="MIT") %>% 
  dplyr::group_by(region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarise(
    oc = mean(opp_cost, na.rm = TRUE),
    oc_ci_l = mean(opp_cost, na.rm = TRUE) - 
      (1.96 * (sd(opp_cost, na.rm = TRUE) / sqrt(nobs(opp_cost)))),
    oc_ci_u = mean(opp_cost, na.rm = TRUE) + 
      (1.96 * (sd(opp_cost, na.rm = TRUE) / sqrt(nobs(opp_cost))))
    ) %>% 
  arrange(region, soiltype, initdenres_collapsed) %>% 
  dplyr::mutate(situation="Worst case")
```



## 4.3. Join data frames

```{r}
oc_both <- rbind(oppcosts_current, oppcosts_worstcase)
rm(bau_vhig, mit_current, oppcosts_current, oppcosts_worstcase)
```


## 4.4. Save data frame
```{r}
write.csv(oc_both, "../output/opp costs_worst case vs current.csv",
          row.names = FALSE)
```

Session info
```{r}
#sessionInfo()
```

