---
title: "Wheat yield - summary stats and data frames for plots"
author: "Alexa Varah"
date: "15/02/2022"
output: html_document
---

# 1. Intro
This script looks at what happens to wheat yield under different scenarios and initial conditions. It answers the following questions:  

1. How much less wheat do MIT strategies produce than BAU and CWW strategies?  

2. For different initial denres, if farmers switched to MIT strategies, what would be the per hectare drop in wheat production? 

3. Is it better for wheat production to switch pre-emptively to MIT, or is it better for wheat production to continue with BAU in the knowledge that weed density will get worse?  
  
Calculate wheat yield from:  
* (i) BAU rotations in LD-HR fields  
* (ii) BAU rotations when LD-HR fields have high weed density  
* (iii) MIT rotations in LD-HR fields    

Definitions of the variables used here:  
  
* **imp** = density estimation imputation (there were 37 (previously 97) imputations for each year of each rotation).    
* **scenario** = three potential future farm management scenarios: Business As Usual (BAU), Continuous Winter Wheat (CWW) or Mitigation of herbicide-resistant black-grass populations (MIT).  
* **region** = north, central and east. These were the regions to which we asked farmers to tailor their MIT strategies.  
* **soiltype** = broad categorisation of soils into heavy/medium or light. These were the soil types to which we asked farmers to tailor their MIT strategies.  
* **initdenres** = initial density and resistance status of a theoretical field. These were the density and resistance states to which we asked farmers to tailor their MIT strategies. L = low; H = high; D = density; R = resistance.  
* **yr** = year of rotation (all rotations were 6 years).  
* **wtd_yield** = weighted crop yield. Only wheat yields are weighted as they are the only crop that responds to black-grass density in ECOMOD.  
* **ww_yield** = wheat yield. OTher crops set to zero.  
* **ww_prod_cost_ww** = Productivity costs for wheat.  
  
# 2. Set up
## 2.1. Load packages & functions
```{r load-packages, message=FALSE}
rm(list=ls())
library(tidyverse)
library(patchwork) # for panel plots
```

Load function to count complete observations
```{r}
nobs <- function(x) length(x[!is.na(x)])
```

## 2.2. Load data
```{r load-data}
ww_3DR <- read.csv("../output/wwyield_data_for_analysis_3DR.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))

ww_3DR_hd <- read.csv("../output/wwyield_data_for_analysis_3DR_hd.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))


ww_allimp <- read.csv("../output/wwyield_data_for_analysis-all_imputations.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres, levels = c("LD-LR", "MD-LR",
                                               "LD-HR", "MD-HR",
                                               "HD-HR", "VD-HR")))

ww_allimp_hd <- read.csv("../output/wwyield_data_for_analysis-all_imputations_hd.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres, levels = c("LD-LR", "MD-LR",
                                               "LD-HR", "MD-HR",
                                               "HD-HR", "VD-HR")))
```


# 3. Summary stats for paper
When calculating mean wheat yield, I average across imputations (this is already done - resulting file is 'wwyield_data_for_analysis_3DR.csv') before averaging across rotations. The order in which we do the averaging will affect what information is contained in the standard deviation. If you do it the other way round (find mean rotation wheat yield THEN average this across imputations), the SD will be that of the imputations (tiny) rather than giving an idea of how wheat yield varies throughout the rotation (bigger). By averaging across imputations first, and then finding the rotation mean, the SD will tell us how wheat yield varies through the rotation. 

## 3.1. Qu 1. How much less wheat do MIT strategies produce than BAU and CWW strategies?  
### Mean annual (across a rotation) wheat yield & productivity costs by scenario
Calculate mean annual wheat yield (and prod costs) first and THEN summarize across regions, soil types and initial den-res categories. This will give variation due to region, soil type and initial den-res rather than the CI also including year-to-year variation.
```{r}
ww_3DR %>% 
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean)))
    ) %>% 
  #ungroup() %>% # makes no difference whether this line is run or not
  dplyr::group_by(scenario) %>% 
  dplyr::summarize(
    ww = mean(ww_mean, na.rm = TRUE),
    ww_cil = mean(ww_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    ww_ciu = mean(ww_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    pc = mean(pc_mean, na.rm = TRUE),
    pc_cil = mean(pc_mean, na.rm = TRUE) - 
      (1.96 * sd(pc_mean, na.rm = TRUE) / sqrt(length(pc_mean))),
    pc_ciu = mean(pc_mean, na.rm = TRUE) + 
      (1.96 * sd(pc_mean, na.rm = TRUE) / sqrt(length(pc_mean)))
    )
```


## 3.2. Qu 2. For different initial denres, if farmers switched to MIT strategies, what would be the per hectare drop in wheat production? 

### Mean annual (across a rotation) wheat yield & productivity costs by scenario and init den-res
Calculate mean annual wheat yield (and prod costs) first and THEN summarize across regions and soil types. This will give variation due to region and soil type, rather than the CI also including year-to-year variation.
```{r}
ww_3DR %>% 
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean)))
    ) %>% 
  dplyr::group_by(scenario, initdenres_collapsed) %>% 
  dplyr::summarize(
    ww = mean(ww_mean, na.rm = TRUE),
    ww_cil = mean(ww_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    ww_ciu = mean(ww_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    pc = mean(pc_mean*(-1), na.rm = TRUE),
    pc_ciu = mean(pc_mean*(-1), na.rm = TRUE) - 
      (1.96 * sd(pc_mean*(-1), na.rm = TRUE) / sqrt(length(pc_mean*(-1)))),
        pc_cil = mean(pc_mean*(-1), na.rm = TRUE) + 
      (1.96 * sd(pc_mean*(-1), na.rm = TRUE) / sqrt(length(pc_mean*(-1))))
    )
```

For the productivity costs, a negative value indicates that MIT wins. 



### What are the productivity costs (of switching to MIT) by region and initdenres category
Find mean annual productivity costs first, THEN average across soil types. This will mean that the CIs reflect variation due to regional differences, rather than also including year-to-year variation. 
```{r}
ww_3DR %>% 
  # find rotation mean
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean)))
    ) %>% 
  # find region mean
  dplyr::group_by(scenario, region, initdenres_collapsed) %>% 
  dplyr::summarize(
    ww = mean(ww_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    ww_ci_u = mean(ww_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    pc = mean(pc_mean*(-1), na.rm = TRUE),
    pc_ci_l = mean(pc_mean*(-1), na.rm = TRUE) - 
      (1.96 * sd(pc_mean*(-1), na.rm = TRUE) / sqrt(length(pc_mean*(-1)))),
    pc_ci_u = mean(pc_mean*(-1), na.rm = TRUE) + 
      (1.96 * sd(pc_mean*(-1), na.rm = TRUE) / sqrt(length(pc_mean*(-1))))
    ) %>% 
  dplyr::filter(scenario=="MIT") %>% 
  dplyr::relocate(scenario, .after = pc_ci_u)
```

For the productivity costs, a negative value indicates that MIT wins.  
95% CIs reflect variation due to soil type within each region.  



#### Show this just for LD-LR fields
```{r}
ww_3DR %>% 
  # find rotation mean
  dplyr::group_by(scenario, region, soiltype, initdenres_collapsed) %>% 
  dplyr::summarize(
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean)))
    ) %>% 
  # find region mean
  dplyr::group_by(scenario, region, initdenres_collapsed) %>% 
  dplyr::summarize(
    ww = mean(ww_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    ww_ci_u = mean(ww_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_mean, na.rm = TRUE) / sqrt(length(ww_mean))),
    pc = mean(pc_mean*(-1), na.rm = TRUE),
    pc_ci_l = mean(pc_mean*(-1), na.rm = TRUE) - 
      (1.96 * sd(pc_mean*(-1), na.rm = TRUE) / sqrt(length(pc_mean*(-1)))),
    pc_ci_u = mean(pc_mean*(-1), na.rm = TRUE) + 
      (1.96 * sd(pc_mean*(-1), na.rm = TRUE) / sqrt(length(pc_mean*(-1))))
    ) %>% 
  dplyr::filter(scenario=="MIT" & initdenres_collapsed =="LD-LR") 
```

For the productivity costs, a negative value indicates that MIT wins. 
95% CIs reflect variation due to soil type within each region.  


# 4. Data frames for plots
## 4.1. Rotation wheat yield, 3 denres
Make data frame for the plot.
```{r}
smrz_rotn_3DR <- ww_3DR %>% 
  dplyr::group_by(scenario, initdenres_collapsed, soiltype, region) %>% 
  dplyr::summarize(
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean)))
    )
```

The CIs in this plot will show the year-to-year variation.

Save this data frame so I can more easily re-make the plot later as it's used in the paper.
```{r, eval=FALSE, echo=FALSE}
write.csv(smrz_rotn_3DR, "../output/data for scatter plot_wheat yield.csv",
          row.names = FALSE)
```



## 4.2. Rotation wheat yield, 3 denres, NO CWW - LD-LR at init HD

Make data frame for the plot.
```{r}
smrz_rotn_3DR_hd <- ww_3DR_hd %>% 
  dplyr::group_by(scenario, initdenres_collapsed, soiltype, region) %>% 
  dplyr::summarize(
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96 * sd(ww_yield_mean, na.rm = TRUE) / sqrt(nobs(ww_yield_mean))),
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96 * sd(prod_cost_mean, na.rm = TRUE) / sqrt(nobs(prod_cost_mean)))
    )
```

The CIs in this plot will show the year-to-year variation.

#### Save data
Save this data frame to make the plot in Script 9.
```{r, eval=FALSE, echo=FALSE}
write.csv(smrz_rotn_3DR_hd, "../output/data for scatter plot_wheat yield_hd.csv",
          row.names = FALSE)
```



# 5. Session info
```{r}
sessionInfo()
```

