---
title: "Scaling up"
author: "Alexa Varah"
date: "31/01/2022"
output: html_document
---

# 1. Intro
This script answers the following questions:  

1. At a national scale, how much less wheat do MIT strategies produce than BAU and CWW strategies?  

2. For different initial den-res states, if farmers switched from BAU to MIT strategies, what would be the drop in wheat production at national and regional scales?  

3. At a national scale, is it better for wheat production to switch pre-emptively to MIT, or is it better for wheat production to continue with BAU in the knowledge that weed density will get worse?  

When calculating mean annual wheat yield, I average across imputations (this is already done - resulting file is 'cerealarea_by_localauthority_and_denres_3DR.csv') before averaging wheat yield across rotations. The SD therefore tells us how wheat yield varies through the rotation.  

# 2. Set up
## 2.1. Load packages
```{r load-packages, message = FALSE}
rm(list=ls())
library(tidyverse) # for easy data manipulation; includes dplyr, ggplot & more
```

## 2.2. Load functions
Function to count complete observations
```{r load-functions}
nobs <- function(x) length(x[!is.na(x)])
```

## 2.3. Load data
Use the summarised economic data created in Script 4b and summarised yield data created in script 5b.
```{r load-data}
# regional cereal areas for each denres state:
cereal <- read.csv("../output/cerealarea_by_localauthority_and_denres_3DR_2021.csv", 
                   header = TRUE) %>% 
  dplyr::mutate(initDR = as.factor(initDR),
                initDR = fct_recode(initDR,
                                    "LD-LR" = "LDLR",
                                    "LD-HR" = "LDHR",
                                    "HD-HR" = "HDHR")) %>% 
  dplyr::rename(initdenres = initDR)

# economic data:
econ_3dr <- read.csv("../output/economic_data_for_analysis_3DR.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario),
    region = factor(region,
                    levels = c("north", "central","east")),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres_collapsed,
                        levels = c("LD-LR", "LD-HR", "HD-HR"))
    ) %>% 
  dplyr::select(-initdenres_collapsed)

# yield data:
ww_3dr <- read.csv("../output/wwyield_data_for_analysis_3DR.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario),
    region = factor(region,
                    levels = c("north", "central","east")),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres_collapsed,
                        levels = c("LD-LR", "LD-HR", "HD-HR"))
    ) %>% 
  dplyr::select(-initdenres_collapsed)

# worst case economic data
bau_vhig <- read.csv("../output/bau_ECOMOD_output_V.csv", header=TRUE) %>% 
  dplyr::select(-Field_no) %>% # remove unnecessary column
  dplyr::rename_with(stringr::str_replace, 
              # add '.' b4 the number in 'crop' colnames:
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  dplyr::rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# worst case productivity costs
pc_both <- read.csv("../output/prod costs_worst case vs current.csv", header = TRUE) %>% 
  dplyr::mutate(
    region = factor(region,
                    levels = c("north", "central","east")),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres_collapsed,
                        levels = c("LD-LR", "LD-HR", "HD-HR"))
    )

# worst case opportunity costs
oc_both <- read.csv("../output/opp costs_worst case vs current.csv", header = TRUE) %>% 
  dplyr::mutate(
    region = factor(region,
                    levels = c("north", "central","east")),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium","light")),
    initdenres = factor(initdenres_collapsed,
                        levels = c("LD-LR", "LD-HR", "HD-HR"))
    )
```

## 2.4. Tidy data
Join economic and yield data.
```{r}
econ_wwyield <- left_join(econ_3dr, ww_3dr %>% 
                            dplyr::select(c(ID, ww_yield_mean:prod_cost_ci_u)),
                          by="ID") %>% 
  dplyr::relocate(initdenres, .after=soiltype)
```

Sort out BAU very high density data.
```{r BAU-worstcase-reshape-tidy-calc-means}
bau_worstcase <- bau_vhig %>%
  # reshape
  tidyr::pivot_longer(
    cols = c(2:85),
    names_to = c(".value", "year"),
    names_sep = '\\.'
    ) %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::arrange(field_name) %>% 
  # make columns for soil, region, initial density etc
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
 
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),

    # recode soil type and region, and specify order of factor levels
    soiltype = dplyr::recode(soiltype,
                      "h" = "heavy",
                      "m" = "medium",
                      "l" = "light"),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium", "light")
                      ),
    region = dplyr::recode(region,
                    "n" = "north",
                    "c" = "central",
                    "e" = "east"),
    region = factor(region,
                    levels = c("north", "central", "east")
                    ),
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "BAU"
    ) %>%
  # make it easier to look at
  dplyr::relocate(scenario, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name) %>% 
  
  # Collapse den-res levels
  dplyr::mutate(
    initdenres_collapsed = fct_recode(
      initdenres, 
      "LD-LR" = "MD-LR",# LD-LR & MD-LR (best case)
      "LD-HR" = "MD-HR",# LD-HR & MD-HR (intermediate case) 
      "HD-HR" = "VD-HR"),# HD-HR & VD-HR (worst case)
    initdenres_collapsed = factor(initdenres_collapsed,
      levels = c("LD-LR", "LD-HR", "HD-HR"))
    ) %>% 
  #for any crop that isn't wheat, assign zero yield
  dplyr::mutate(ww_yield = ifelse(stringr::str_detect(crop, 'wheat'),yield, 0)) %>% 
  # Calculate mean gross profit and wheat yield across the new den-res levels 
  # (include 'crop' in the grouping command just to retain that variable - 
  # it doesn't change the calculations if I omit it)
  group_by(scenario, region, soiltype, year, initdenres_collapsed, crop) %>% 
  dplyr::mutate(
    # yield
    ww_yld_mean = mean(ww_yield, na.rm = TRUE),
    ww_yld_ci_l = mean(ww_yield, na.rm = TRUE) - 
      (1.96 * sd(ww_yield, na.rm = TRUE) / sqrt(nobs(ww_yield))),
    ww_yld_ci_u = mean(ww_yield, na.rm = TRUE) + 
      (1.96 * sd(ww_yield, na.rm = TRUE) / sqrt(nobs(ww_yield))),
    # gross profit
    gp_mean = mean(grossprof, na.rm = TRUE),
    gp_ci_l = mean(grossprof, na.rm = TRUE) - 
      (1.96 * sd(grossprof, na.rm = TRUE) / sqrt(nobs(grossprof))),
    gp_ci_u = mean(grossprof, na.rm = TRUE) + 
      (1.96 * sd(grossprof, na.rm = TRUE) / sqrt(nobs(grossprof)))
    ) %>%
  dplyr::select(scenario, region, soiltype, year, initdenres_collapsed, crop, 
                ww_yld_mean, ww_yld_ci_l, ww_yld_ci_u, 
                gp_mean, gp_ci_l, gp_ci_u) %>% 
  dplyr::distinct(scenario, region, soiltype, initdenres_collapsed, year, .keep_all = TRUE) %>% 
  dplyr::arrange(scenario, region, soiltype, initdenres_collapsed, year)
```



# 3. Scale up
## 3.1. Yield & economic data
### Calculate mean annual ww yield, prod costs & opp costs per initdenres and region
In other words, calculate the mean values across a 6-year rotation for each den-res state in each region. Collapse across soil types.  
```{r mean-values-per-denres-and-region}
oc_pc_annual_region <- econ_wwyield %>% 
  dplyr::filter(scenario=="MIT") %>% 
  # find rotation mean first
  dplyr::group_by(region, soiltype, initdenres) %>% 
  dplyr::summarize(
    # wheat yield
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96*(sd(ww_yield_mean, na.rm = TRUE)/sqrt(nobs(ww_yield_mean)))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96*(sd(ww_yield_mean, na.rm = TRUE)/sqrt(nobs(ww_yield_mean)))),
    # productivity cost
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96*(sd(prod_cost_mean, na.rm = TRUE)/sqrt(nobs(prod_cost_mean)))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96*(sd(prod_cost_mean, na.rm = TRUE)/sqrt(nobs(prod_cost_mean)))),
    # opportunity cost
    oc_mean = mean(wtd_opp_cost_mean, na.rm = TRUE),
    oc_ci_l = mean(wtd_opp_cost_mean, na.rm = TRUE) - 
      (1.96*(sd(wtd_opp_cost_mean, na.rm = TRUE)/sqrt(nobs(wtd_opp_cost_mean)))),
    oc_ci_u = mean(wtd_opp_cost_mean, na.rm = TRUE) + 
      (1.96*(sd(wtd_opp_cost_mean, na.rm = TRUE)/sqrt(nobs(wtd_opp_cost_mean))))    
    ) %>% 
  # then find average value by region and initdenres
  group_by(region, initdenres) %>%
  dplyr::summarise(
    # wheat yield
    ww = mean(ww_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_mean, na.rm = TRUE) - 
      (1.96*(sd(ww_mean, na.rm = TRUE)/sqrt(nobs(ww_mean)))),
    ww_ci_u = mean(ww_mean, na.rm = TRUE) + 
      (1.96*(sd(ww_mean, na.rm = TRUE)/sqrt(nobs(ww_mean)))),
    # productivity cost
    pc = mean(pc_mean*(-1), na.rm = TRUE),
    pc_var = var(pc_mean, na.rm = TRUE),
    pc_ci_l = mean(pc_mean*(-1), na.rm = TRUE) - 
      (1.96*(sd(pc_mean*(-1), na.rm = TRUE)/sqrt(nobs(pc_mean*(-1))))),
    pc_ci_u = mean(pc_mean*(-1), na.rm = TRUE) + 
      (1.96*(sd(pc_mean*(-1), na.rm = TRUE)/sqrt(nobs(pc_mean*(-1))))),
    # opportunity cost
    oc = mean(oc_mean*(-1), na.rm = TRUE),
    oc_var = var(oc_mean, na.rm = TRUE),
    oc_ci_l = mean(oc_mean*(-1), na.rm = TRUE) - 
      (1.96*(sd(oc_mean*(-1), na.rm = TRUE)/sqrt(nobs(oc_mean*(-1))))),
    oc_ci_u = mean(oc_mean*(-1), na.rm = TRUE) + 
      (1.96*(sd(oc_mean*(-1), na.rm = TRUE)/sqrt(nobs(oc_mean*(-1)))))
    ) 

oc_pc_annual_region
```

For opp and prod costs, a negative value means that MIT wins.  
95% confidence intervals indicate variation across soil types within a region.  


### Calculate mean annual ww yield, prod costs & opp costs per initdenres across all regions
In other words, calculate the mean values across a 6-year rotation for each den-res state, collapsed across all regions and soil types.
```{r mean-values-per-denres}
oc_pc_annual_total <- econ_wwyield %>% 
  dplyr::filter(scenario=="MIT") %>% 
  # find rotation mean first
  dplyr::group_by(region, soiltype, initdenres) %>% 
  dplyr::summarize(
    # wheat yield
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96*(sd(ww_yield_mean, na.rm = TRUE)/sqrt(nobs(ww_yield_mean)))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96*(sd(ww_yield_mean, na.rm = TRUE)/sqrt(nobs(ww_yield_mean)))),
    # productivity cost
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96*(sd(prod_cost_mean, na.rm = TRUE)/sqrt(nobs(prod_cost_mean)))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96*(sd(prod_cost_mean, na.rm = TRUE)/sqrt(nobs(prod_cost_mean)))),
    # opportunity cost
    oc_mean = mean(wtd_opp_cost_mean, na.rm = TRUE),
    oc_ci_l = mean(wtd_opp_cost_mean, na.rm = TRUE) - 
      (1.96*(sd(wtd_opp_cost_mean, na.rm = TRUE)/sqrt(nobs(wtd_opp_cost_mean)))),
    oc_ci_u = mean(wtd_opp_cost_mean, na.rm = TRUE) + 
      (1.96*(sd(wtd_opp_cost_mean, na.rm = TRUE)/sqrt(nobs(wtd_opp_cost_mean))))    
    ) %>%  
  # then find mean value for each initdenres
  group_by(initdenres) %>%
  dplyr::summarise(
    # wheat yield
    ww = mean(ww_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_mean, na.rm = TRUE) - 
      (1.96*(sd(ww_mean, na.rm = TRUE)/sqrt(nobs(ww_mean)))),
    ww_ci_u = mean(ww_mean, na.rm = TRUE) + 
      (1.96*(sd(ww_mean, na.rm = TRUE)/sqrt(nobs(ww_mean)))),
    # productivity cost
    pc = mean(pc_mean*(-1), na.rm = TRUE),
    pc_var = var(pc_mean, na.rm = TRUE),
    pc_ci_l = mean(pc_mean*(-1), na.rm = TRUE) - 
      (1.96*(sd(pc_mean*(-1), na.rm = TRUE)/sqrt(nobs(pc_mean*(-1))))),
    pc_ci_u = mean(pc_mean*(-1), na.rm = TRUE) + 
      (1.96*(sd(pc_mean*(-1), na.rm = TRUE)/sqrt(nobs(pc_mean*(-1))))),
    # opportunity cost
    oc = mean(oc_mean*(-1), na.rm = TRUE),
    oc_var = var(oc_mean, na.rm = TRUE),
    oc_ci_l = mean(oc_mean*(-1), na.rm = TRUE) - 
      (1.96*(sd(oc_mean*(-1), na.rm = TRUE)/sqrt(nobs(oc_mean*(-1))))),
    oc_ci_u = mean(oc_mean*(-1), na.rm = TRUE) + 
      (1.96*(sd(oc_mean*(-1), na.rm = TRUE)/sqrt(nobs(oc_mean*(-1)))))
    ) %>% 
  dplyr::mutate(region = "all") %>%
  dplyr::relocate(region, .before = initdenres)

oc_pc_annual_total
```


For opp and prod costs, a negative value means that MIT wins.  
95% confidence intervals indicate variation across regions and soil types.  


### Calculate mean annual ww yield, prod costs & opp costs per region across all initdenres
In other words, calculate the mean values across a 6-year rotation for each region, collapsed across all den-res states and soil types.
```{r mean-values-per-denres-repeated}
oc_pc_annual_allDR <- econ_wwyield %>% 
  dplyr::filter(scenario=="MIT") %>% 
  # find rotation mean first
  dplyr::group_by(region, soiltype, initdenres) %>% 
  dplyr::summarize(
    # wheat yield
    ww_mean = mean(ww_yield_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_yield_mean, na.rm = TRUE) - 
      (1.96*(sd(ww_yield_mean, na.rm = TRUE)/sqrt(nobs(ww_yield_mean)))),
    ww_ci_u = mean(ww_yield_mean, na.rm = TRUE) + 
      (1.96*(sd(ww_yield_mean, na.rm = TRUE)/sqrt(nobs(ww_yield_mean)))),
    # productivity cost
    pc_mean = mean(prod_cost_mean, na.rm = TRUE),
    pc_ci_l = mean(prod_cost_mean, na.rm = TRUE) - 
      (1.96*(sd(prod_cost_mean, na.rm = TRUE)/sqrt(nobs(prod_cost_mean)))),
    pc_ci_u = mean(prod_cost_mean, na.rm = TRUE) + 
      (1.96*(sd(prod_cost_mean, na.rm = TRUE)/sqrt(nobs(prod_cost_mean)))),
    # opportunity cost
    oc_mean = mean(wtd_opp_cost_mean, na.rm = TRUE),
    oc_ci_l = mean(wtd_opp_cost_mean, na.rm = TRUE) - 
      (1.96*(sd(wtd_opp_cost_mean, na.rm = TRUE)/sqrt(nobs(wtd_opp_cost_mean)))),
    oc_ci_u = mean(wtd_opp_cost_mean, na.rm = TRUE) + 
      (1.96*(sd(wtd_opp_cost_mean, na.rm = TRUE)/sqrt(nobs(wtd_opp_cost_mean))))    
    ) %>% 
  # then find regional mean
  group_by(region) %>%
  dplyr::summarise(
    # wheat yield
    ww = mean(ww_mean, na.rm = TRUE),
    ww_ci_l = mean(ww_mean, na.rm = TRUE) - 
      (1.96*(sd(ww_mean, na.rm = TRUE)/sqrt(nobs(ww_mean)))),
    ww_ci_u = mean(ww_mean, na.rm = TRUE) + 
      (1.96*(sd(ww_mean, na.rm = TRUE)/sqrt(nobs(ww_mean)))),
    # productivity cost
    pc = mean(pc_mean*(-1), na.rm = TRUE),
    pc_var = var(pc_mean, na.rm = TRUE),
    pc_ci_l = mean(pc_mean*(-1), na.rm = TRUE) - 
      (1.96*(sd(pc_mean*(-1), na.rm = TRUE)/sqrt(nobs(pc_mean*(-1))))),
    pc_ci_u = mean(pc_mean*(-1), na.rm = TRUE) + 
      (1.96*(sd(pc_mean*(-1), na.rm = TRUE)/sqrt(nobs(pc_mean*(-1))))),
    # opportunity cost
    oc = mean(oc_mean*(-1), na.rm = TRUE),
    oc_var = var(oc_mean, na.rm = TRUE),
    oc_ci_l = mean(oc_mean*(-1), na.rm = TRUE) - 
      (1.96*(sd(oc_mean*(-1), na.rm = TRUE)/sqrt(nobs(oc_mean*(-1))))),
    oc_ci_u = mean(oc_mean*(-1), na.rm = TRUE) + 
      (1.96*(sd(oc_mean*(-1), na.rm = TRUE)/sqrt(nobs(oc_mean*(-1)))))
    ) %>% 
  dplyr::mutate(initdenres = "all") %>%
  dplyr::relocate(region, initdenres)

oc_pc_annual_allDR
```

For opp and prod costs, a negative value means that MIT wins.  
95% confidence intervals indicate variation across regions and soil types and init den res levels.  



### Join 'individual regions' yield data to 'all regions' data
```{r}
yld_oc_pc <- rbind(oc_pc_annual_region, oc_pc_annual_allDR, oc_pc_annual_total)%>% 
  dplyr::mutate(ID = paste(region, initdenres, sep = "_")) %>% 
  dplyr::relocate(ww:ww_ci_u, .after = oc_ci_u) %>% 
  dplyr::relocate(oc:oc_ci_u, .after = initdenres)
```

## 3.2. Cereal data
##### Sum area of each density state per region
```{r message=FALSE}
cereal_region <- cereal %>% 
  dplyr::group_by(region, initdenres) %>% 
  dplyr::summarise(cereal_area = sum(cereal_area_in_denres_state))
```


##### Sum area of each density state across all regions
```{r}
cereal_total <- cereal %>% 
  dplyr::group_by(initdenres) %>% 
  dplyr::summarise(cereal_area = sum(cereal_area_in_denres_state)) %>% 
  dplyr::mutate(region="all") %>% 
  dplyr::relocate(region)
```


##### Sum area of all density states combined to just give regional area
```{r}
cereal_allDS_region <- cereal %>% 
  dplyr::group_by(region) %>% 
  dplyr::summarise(cereal_area = sum(cereal_area_in_denres_state)) %>% 
  dplyr::mutate(initdenres="all") %>% 
  dplyr::relocate(region, initdenres)
```


##### Join 'individual regions' cereal data to 'all regions' cereal data
```{r}
cereal_forjoin <- rbind(cereal_region, cereal_total, cereal_allDS_region) %>% 
  dplyr::mutate(ID = paste(region, initdenres, sep = "_"))
```



## 3.3. Scaled-up data
##### Calculate scaled-up costs for each region
To do this, add ww yield, productivity costs and opportunity costs onto the cereal data and calculate scaled-up costs.
```{r calculate-scaled-up-costs}
yld_pc_oc_scaled <- dplyr::inner_join(cereal_forjoin, yld_oc_pc, by = "ID") %>% 
  dplyr::mutate(
    # ww yield
    ww_reg = ww*cereal_area,
    ww_reg_ci_l = ww_ci_l*cereal_area,
    ww_reg_ci_u = ww_ci_u*cereal_area,
    # productivity cost
    pc_reg = pc*cereal_area,
    pc_reg_ci_l = pc_ci_l*cereal_area,
    pc_reg_ci_u = pc_ci_u*cereal_area,
    # opportunity cost
    oc_reg = oc*cereal_area,
    oc_reg_ci_l = oc_ci_l*cereal_area,
    oc_reg_ci_u = oc_ci_u*cereal_area,
    # specify order of factor levels
    region = factor(
      region.x, levels = c("north", "central", "east", "all")),
    initdenres = factor(
      initdenres.x, levels = c("LD-LR", "LD-HR", "HD-HR", "all"))
    ) %>% 
  dplyr::select(-c(region.x, initdenres.x, region.y, initdenres.y, ID)) %>% 
  dplyr::relocate(region, initdenres) %>% 
  dplyr::arrange(region, initdenres) %>% 
  #dplyr::select(-c(ww_mean:oc_ci_u))
  dplyr::relocate(oc_reg:oc_reg_ci_u, .before = pc_reg)%>% 
  dplyr::relocate(oc:oc_ci_u, .before = pc) %>% 
  dplyr::relocate(ww_reg:ww_reg_ci_u, .before = oc) 

yld_pc_oc_scaled
```

For the last three rows (region = 'all'), 95% confidence intervals indicate variation across regions and soil types. For all other rows, 95% confidence intervals indicate variation across soil types within a region.  
For opp and prod costs, a negative value means that MIT wins.  
  

## 3.4. Clean up
```{r}
rm(bau_vhig, bau_worstcase, econ_3dr, econ_wwyield, 
   cereal_region, cereal_total, cereal_allDS_region,
   oc_pc_annual_region, oc_pc_annual_total, oc_pc_annual_allDR,
   ww_3dr, yld_oc_pc)
```



# 4. Inspect data / summary stats
## ----

## Qus 1 & 2
### PC & OC, national scale, 3 den res states  
```{r}
yld_pc_oc_scaled %>% 
  dplyr::filter(region == "all") %>% 
  dplyr::select(c(region, initdenres, oc_reg:pc_reg_ci_u)) %>% 
  dplyr::mutate(across(where(is.numeric), round, 0))
```

For opp and prod costs, a negative value means that MIT wins.  
95% confidence intervals indicate variation across regions and soil types.  


### PC & OC, regional scale, 3 den res states
```{r}
yld_pc_oc_scaled %>% 
  dplyr::filter(!region == "all" & !initdenres == "all") %>% 
  dplyr::select(c(region, initdenres, oc_reg:pc_reg_ci_u)) %>% 
  dplyr::mutate(across(where(is.numeric), round, 0))
```

For opp and prod costs, a negative value means that MIT wins.  
95% confidence intervals indicate variation across soil types within a region.  


### PC & OC, regional scale, across all den res states  
```{r}
yld_pc_oc_scaled %>% 
  dplyr::filter(!region == "all" & initdenres == "all") %>% 
  dplyr::select(c(region, initdenres, oc_reg:pc_reg_ci_u)) %>% 
  dplyr::mutate(across(where(is.numeric), round, 0))
```

For opp and prod costs, a negative value means that MIT wins.  
95% confidence intervals indicate variation across initdenres levels and soil types.  




## ----
## Qu 3: At a national scale, how much wheat is lost by switching pre-emptively to MIT, and how much wheat is lost if we continue with BAU in the knowledge that weed density will get worse? 
For this, use the data frame containing worst-case and current costs.

### Calculate mean annual worst case prod costs per initdenres and region
In other words, calculate the mean values across a 6-year rotation for each den-res state in each region. Collapse across soil types.
```{r mean-worstcase-pc-values-per-denres-and-region}
pc_both_region <- pc_both %>% 
  group_by(region, initdenres_collapsed, situation) %>%
  dplyr::summarise(
    pc_mean = mean(pc*(-1), na.rm = TRUE),
    pc_ci_l = mean(pc*(-1), na.rm = TRUE) - 
      (1.96*(sd(pc*(-1), na.rm = TRUE)/sqrt(nobs(pc*(-1))))),
    pc_ci_u = mean(pc*(-1), na.rm = TRUE) + 
      (1.96*(sd(pc*(-1), na.rm = TRUE)/sqrt(nobs(pc*(-1)))))
    ) %>% 
  dplyr::rename(initdenres = initdenres_collapsed) %>% 
  dplyr::mutate(initdenres = factor(initdenres,
                                    levels = c("LD-LR", "LD-HR", "HD-HR"))) %>% 
  dplyr::arrange(region, initdenres)

pc_both_region
```


For opp and prod costs, a negative value means that MIT wins.  
95% CIs show variation due to soil type.  
  

### Calculate mean annual prod costs per initdenres across all regions
In other words, calculate the mean prod costs across a 6-year rotation for each den-res state, collapsed across all regions and soil types.
```{r mean-prod-costs-per-denres}
pc_both_total <- pc_both %>% 
  group_by(initdenres_collapsed, situation) %>%
  dplyr::summarise(
    pc_mean = mean(pc*(-1), na.rm = TRUE),
    pc_ci_l = mean(pc*(-1), na.rm = TRUE) - 
      (1.96*(sd(pc*(-1), na.rm = TRUE)/sqrt(nobs(pc*(-1))))),
    pc_ci_u = mean(pc*(-1), na.rm = TRUE) + 
      (1.96*(sd(pc*(-1), na.rm = TRUE)/sqrt(nobs(pc*(-1)))))
    ) %>% 
  dplyr::mutate(region = "all") %>%
  dplyr::rename(initdenres = initdenres_collapsed) %>% 
  dplyr::relocate(region, .before = initdenres) %>% 
  dplyr::mutate(initdenres = factor(initdenres,
                                    levels = c("LD-LR", "LD-HR", "HD-HR"))) %>% 
  dplyr::arrange(region, initdenres)

pc_both_total
```

For opp and prod costs, a negative value means that MIT wins.  
95% CIs show variation due to soil type and region.  
  
  


### Join 'individual regions' prod costs data to 'all regions' prod costs data
```{r}
pc_forjoin <- rbind(pc_both_region, pc_both_total)
rm(pc_both_region, pc_both_total)
```


### Calculate scaled-up worst case prod costs for each region
To do this, add worst case productivity costs onto the cereal data and calculate scaled-up costs.
```{r calculate-worstcase-scaled-up-prod-costs}
pc_worstcase_scaled <- dplyr::inner_join(cereal_forjoin, pc_forjoin, by = c("region", "initdenres")) %>% 
  dplyr::mutate(
    # productivity cost
    pc_reg = pc_mean*cereal_area,
    pc_reg_ci_l = pc_ci_l*cereal_area,
    pc_reg_ci_u = pc_ci_u*cereal_area,
    # specify order of factor levels
    region = factor(
      region, levels = c("north", "central", "east", "all")),
    initdenres = factor(
      initdenres, levels = c("LD-LR", "LD-HR", "HD-HR"))
    ) %>% 
  dplyr::arrange(region, initdenres) %>% 
  dplyr::select(-c(pc_mean:pc_ci_u))

rm(pc_forjoin)
```




### Answer - mean pc in all regions, across all denres levels
```{r}
pc_worstcase_scaled %>% 
  dplyr::group_by(region, situation) %>% 
  dplyr::summarise(
    pc_mean = mean(pc_reg, na.rm = TRUE),
    pc_ci_l = mean(pc_reg, na.rm = TRUE) - 
      (1.96*(sd(pc_reg, na.rm = TRUE)/sqrt(nobs(pc_reg)))),
    pc_ci_u = mean(pc_reg, na.rm = TRUE) + 
      (1.96*(sd(pc_reg, na.rm = TRUE)/sqrt(nobs(pc_reg))))
  ) %>% 
  dplyr::filter(region == "all")
```

For opp and prod costs, a negative value means that MIT wins.  
95% CIs show variation due to initdenres.  


### Answer - mean pc in all regions, for each denres level
```{r}
pc_worstcase_scaled %>% 
  dplyr::filter(region == "all") %>% 
  dplyr::select(-cereal_area) %>% 
  dplyr::arrange(situation) %>% 
  dplyr::select(-ID)
```

For opp and prod costs, a negative value means that MIT wins.  
Where region = 'all', 95% CIs show variation due to soil type and region.   



## Qu 4: At a national scale, what are the financial implications of switching pre-emptively to MIT, and what are they if we continue with BAU in the knowledge that weed density will get worse? 
For this, use the data frame containing worst-case and current costs.

### Calculate mean annual worst case opp costs per initdenres and region
In other words, calculate the mean values across a 6-year rotation for each den-res state in each region. Collapse across soil types.
```{r mean-worstcase-oc-values-per-denres-and-region}
oc_both_region <- oc_both %>% 
  group_by(region, initdenres_collapsed, situation) %>%
  dplyr::summarise(
    oc_mean = mean(oc*(-1), na.rm = TRUE),
    oc_ci_l = mean(oc*(-1), na.rm = TRUE) - 
      (1.96*(sd(oc*(-1), na.rm = TRUE)/sqrt(nobs(oc*(-1))))),
    oc_ci_u = mean(oc*(-1), na.rm = TRUE) + 
      (1.96*(sd(oc*(-1), na.rm = TRUE)/sqrt(nobs(oc*(-1)))))
    ) %>% 
  dplyr::rename(initdenres = initdenres_collapsed) %>% 
  dplyr::mutate(initdenres = factor(initdenres,
                                    levels = c("LD-LR", "LD-HR", "HD-HR"))) %>% 
  dplyr::arrange(region, initdenres)

oc_both_region
```


For opp costs, a negative value means that MIT wins.  
95% CIs show variation due to soil type.  
  

### Calculate mean annual opp costs per initdenres across all regions
In other words, calculate the mean opp costs across a 6-year rotation for each den-res state, collapsed across all regions and soil types.
```{r mean-opp-costs-per-denres}
oc_both_total <- oc_both %>% 
  group_by(initdenres_collapsed, situation) %>%
  dplyr::summarise(
    oc_mean = mean(oc*(-1), na.rm = TRUE),
    oc_ci_l = mean(oc*(-1), na.rm = TRUE) - 
      (1.96*(sd(oc*(-1), na.rm = TRUE)/sqrt(nobs(oc*(-1))))),
    oc_ci_u = mean(oc*(-1), na.rm = TRUE) + 
      (1.96*(sd(oc*(-1), na.rm = TRUE)/sqrt(nobs(oc*(-1)))))
    ) %>% 
  dplyr::mutate(region = "all") %>%
  dplyr::rename(initdenres = initdenres_collapsed) %>% 
  dplyr::relocate(region, .before = initdenres) %>% 
  dplyr::mutate(initdenres = factor(initdenres,
                                    levels = c("LD-LR", "LD-HR", "HD-HR"))) %>% 
  dplyr::arrange(region, initdenres)

oc_both_total
```

For opp costs, a negative value means that MIT wins.  
95% CIs show variation due to soil type and region.  
  
  


### Join 'individual regions' opp costs data to 'all regions' opp costs data
```{r}
oc_forjoin <- rbind(oc_both_region, oc_both_total)
rm(oc_both_region, oc_both_total)
```


### Calculate scaled-up worst case opp costs for each region
To do this, add worst case opportunity costs onto the cereal data and calculate scaled-up costs.
```{r calculate-worstcase-scaled-up-opp-costs}
oc_worstcase_scaled <- dplyr::inner_join(cereal_forjoin, oc_forjoin, by = c("region", "initdenres")) %>% 
  dplyr::mutate(
    # oppuctivity cost
    oc_reg = oc_mean*cereal_area,
    oc_reg_ci_l = oc_ci_l*cereal_area,
    oc_reg_ci_u = oc_ci_u*cereal_area,
    # specify order of factor levels
    region = factor(
      region, levels = c("north", "central", "east", "all")),
    initdenres = factor(
      initdenres, levels = c("LD-LR", "LD-HR", "HD-HR"))
    ) %>% 
  dplyr::arrange(region, initdenres) %>% 
  dplyr::select(-c(oc_mean:oc_ci_u))

rm(cereal_forjoin, oc_forjoin)
```




### Answer - mean oc in all regions, across all denres levels
```{r}
oc_worstcase_scaled %>% 
  dplyr::group_by(region, situation) %>% 
  dplyr::summarise(
    oc_mean = mean(oc_reg, na.rm = TRUE),
    oc_ci_l = mean(oc_reg, na.rm = TRUE) - 
      (1.96*(sd(oc_reg, na.rm = TRUE)/sqrt(nobs(oc_reg)))),
    oc_ci_u = mean(oc_reg, na.rm = TRUE) + 
      (1.96*(sd(oc_reg, na.rm = TRUE)/sqrt(nobs(oc_reg))))
  ) %>% 
  dplyr::filter(region == "all")
```

For opp costs, a negative value means that MIT wins.  
95% CIs show variation due to initdenres.  


### Answer - mean oc in all regions, for each denres level
```{r}
oc_worstcase_scaled %>% 
  dplyr::filter(region == "all") %>% 
  dplyr::select(-cereal_area) %>% 
  dplyr::arrange(situation) %>% 
  dplyr::select(-ID)
```

For opp costs, a negative value means that MIT wins.  
Where region = 'all', 95% CIs show variation due to soil type and region.   



## Calculate cereal area for each county and region

### County areas
```{r}
cereal %>%
  dplyr::select(region, DEFRA_county_or_unitary_authority, my_counties, cereals_area_2021_ha) %>% 
  distinct(region, DEFRA_county_or_unitary_authority, .keep_all = TRUE) %>%
  dplyr::group_by(my_counties) %>% 
  dplyr::summarise(total_area = sum(cereals_area_2021_ha))
```

### Region areas
```{r}
cereal %>%
  dplyr::select(region, DEFRA_county_or_unitary_authority, cereals_area_2021_ha) %>% 
  distinct(region, DEFRA_county_or_unitary_authority, .keep_all = TRUE) %>% 
  dplyr::group_by(region) %>% 
  dplyr::summarise(total_area = sum(cereals_area_2021_ha))
```
