---
title: "Sensitivity anslysis - run ECOMOD"
author: "Alexa Varah"
date: "11/02/2022"
output: html_document
---

This script runs ECOMOD with upper and lower yield penalty limits. Limits for this sensitivity analysis are the same as those used in the sensitivity analysis in Varah et. al., 2020, and are given in table S10 in the supplementary info in that paper.  

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
rm(list=ls())
pkgs <- c("tidyverse" # for data manipulation (includes dplyr, tidyr, stringr, 
                       # ggplot2, purr, tibble, readr, forcats)
          ,"knitr" # for generating tables
          ,"kableExtra" # for generating tables
          ,"readxl" # for reading in Excel workbooks / spreadsheets
          )
vapply(pkgs, library, logical(1), character.only = TRUE, logical.return = TRUE,
       quietly = TRUE)
```

# Yield penalty limits  
These values are given in Table S2 in the Supplementary Info.  
  
Specify the yield penalties to be used in the sensitivity analysis.  
```{r make-yield-penalty-dataframe}
yldpen.tbl <- data.frame(
  `Black-grass density state` = c("low", "medium", "high", "very high"),
  `Black-grass density (plants per 20x20m grid cell)` = 
    c("1 - 160", "161 - 450", "451 - 1450", ">1450"),
  `lowest value` = c("0.00", "0.00", "0.00", "13.02"),
  `highest value` = c("0.00", "5.14", "28.10", "68.90"),
  `lowest value` = c("0.00", "0.00", "0.00", "13.00"),
  `highest value` = c("0.00", "5.14", "45.00", "70.00")
  )
```

Pass the data frame to kable to show the yield penalty limits in a table.
```{r make-table, echo = FALSE}

kable(yldpen.tbl,
      # Set column headers (N.B. must match the vector names specified above)
      col.names = c("Black-grass density state",
                    "Black-grass density (plants per 20x20m grid cell)",
                    "lowest \nvalue",
                    "highest \nvalue",
                    "lowest \nvalue",
                    "highest \nvalue"
                    ),
      align = c('l', 'l', 'r', 'r', 'r', 'r'),
      # The following line forces the font to be black (kable_styling default is white font).
      # You don't need this line if you use kable_paper or other kable options 
      # such as _material, _minimal, _classic, _paper etc.
      # Adding 'escape = FALSE' allows line breaks within cells; otherwise, 
      # the '<br>' in column text is just printed as text.
      format = "html", escape = FALSE, table.attr = "style = \"color: black;\""
      #) %>% 
      ) %>%
  # Specify column widths
  column_spec(column = 1, width = "1.1in") %>%
  column_spec(column = 2, width = "2in") %>%
  column_spec(column = c(3:6), width = "1.1in") %>% 
  # Specify the look of the table
  kable_styling(bootstrap_options = c( "hover", "responsive", 
                                       font_size = 10, fixed_thead = T)) %>% 
  # Add header row above existing headers for lowest and highest value columns
  add_header_above(
    c(
    " " = 2, # nothing above the first 2 columns
    "Limits suggested by our model \n(% reduction)" = 2, #header for cols 3-4
    "Yield penalties used in sensitivity analysis (% reduction)" = 2 # cols 5-6
    )
    ) 
  
```

# Load ECOMOD 

It takes ages to load ECOMOD in R Markdown so it's not included here. Load ECOMOD versions from script 'Sensitivity Analyses_01.ECOMOD.R' before continuing here. There are 4 versions: 2 with the lower yield penalties, one each with yield set to 'estimate' and 'actual'; and 2 with the higher yield penalties, one each with yield set to 'estimate' and 'actual.'

File 'Sensitivity Analyses_01. Load ECOMOD.R' contains the 4 ECOMOD functions used here.
``` {r ECOMOD, purl=FALSE}
source("07. Sensitivity Analyses - ECOMOD.R")
```


# Run ECOMOD
Run each input file through ECOMOD twice: once with yield set to 'estimate' and once with yield set to 'actual.  

## MIT scenario

Because there are crops in the Mitigation strategies that ECOMOD can't model 
(e.g. spring oats), we read in two versions of the MIT strategies. One version 
has yield set to 'actual', in which average yields for spring oats are given. 
The second version has yield set to 'estimate', so ECOMOD will estimate yields.
  
Read in the raw data.
```{r MIT-raw-data}
mit_est = read_xlsx("../data/InputData_FF_ECOMOD&CFT_2021-12-03.xlsx",3) %>% 
  select(-"lookup_ref") %>%  # remove 'lookup_ref' column
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) # soil texture needs 2 decimal places

#write.csv(mit_est,'output/sensitivity analyses/sens-analy_lower_MIT_ECOMOD_inputdata_estimated-yield.csv')

mit_act = read_xlsx("../data/InputData_FF_ECOMOD&CFT_2021-12-03.xlsx",4) %>% 
  select(-"lookup_ref") %>%  # remove 'lookup_ref' column
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) # soil texture needs 2 decimal places

#write.csv(ff_act,'output/ff_ECOMOD_inputdata_actual-yield.csv')
```

Create input files for each black-grass density state.
```{r MIT-create-input-files}
# LOW / ABSENT
mit_l_est <- mit_est %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>%
  # remove extra 'row identifier' column added by R when reading in the file:
  #dplyr::select(-X) %>% 
  data.frame()

mit_l_act <- mit_act %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>% 
  # remove extra 'row identifier' column added by R when reading in the file:
  #dplyr::select(-X) %>% 
  data.frame()

# MEDIUM
mit_m_est = mit_l_est %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

mit_m_act = mit_l_act %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

# HIGH
mit_h_est = mit_l_est %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% "low", "high"))) %>% 
  data.frame()

mit_h_act = mit_l_act %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% "low", "high"))) %>% 
  data.frame()

# VERY HIGH
mit_v_est = mit_l_est %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% "low", "veryhigh"))) %>% 
  data.frame()

mit_v_act = mit_l_act %>%
  dplyr::mutate(across(starts_with('blackgrass'), 
                       ~replace(., . %in% "low", "veryhigh"))) %>% 
  data.frame()
```

## Sensitivity analysis - lower limits to yield penalties
  
Run input files through ECOMOD
  
### Low/absent model run

**Estimated yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-lowrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_low-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_l_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)
  # 52 secs

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-lowrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_low-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_l_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r lower-sens-analy-MIT-lowrun-combine}
# Read in the ECOMOD output files.
est_l <- read.csv("../output/sensitivity analyses/MIT_lower_low-run_est.csv", 
                  header=T)
# The 'actual' file only has rows containing spring oats
act_l <- read.csv('../output/sensitivity analyses/MIT_lower_low-run_act.csv', 
                  header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_l_1to4 <- act_l %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_l_to_merge <- est_l %>% 
  dplyr::select(!Field_no)

low_den_output1 <- rows_update(
  est_l_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_l_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_l_5to6 <- act_l %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

low_den_output <- rows_update(
  low_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_l_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(low_den_output,
          '../output/sensitivity analyses/MIT_lower_L_combined.csv')

rm(act_l_1to4)
rm(est_l_to_merge)
rm(low_den_output1)
rm(act_l_5to6)
rm(act_l)
rm(est_l)
```
  
  
### Medium model run

**Estimated yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-medrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_med-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_m_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-medrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_med-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_m_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)
 
rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r lower-sens-analy-MIT-medrun-combine}
# Read in the ECOMOD output files.
est_m <- read.csv('../output/sensitivity analyses/MIT_lower_med-run_est.csv', 
                  header=T)
# The 'actual' file only has rows containing spring oats
act_m <- read.csv('../output/sensitivity analyses/MIT_lower_med-run_act.csv', 
                  header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_m_1to4 <- act_m %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_m_to_merge <- est_m %>% 
  dplyr::select(!Field_no)

med_den_output1 <- rows_update(
  est_m_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_m_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_m_5to6 <- act_m %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

med_den_output <- rows_update(
  med_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_m_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(med_den_output,
          '../output/sensitivity analyses/MIT_lower_M_combined.csv')

rm(act_m_1to4)
rm(est_m_to_merge)
rm(med_den_output1)
rm(act_m_5to6)
rm(act_m)
rm(est_m)
```
  
  
### High model run

**Estimated yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-highrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_high-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_h_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-highrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_high-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_h_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r lower-sens-analy-MIT-highrun-combine}
# Read in the ECOMOD output files.
est_h <- read.csv('../output/sensitivity analyses/MIT_lower_high-run_est.csv', 
                  header=T)
# The 'actual' file only has rows containing spring oats
act_h <- read.csv('../output/sensitivity analyses/MIT_lower_high-run_act.csv', 
                  header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_h_1to4 <- act_h %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_h_to_merge <- est_h %>% 
  dplyr::select(!Field_no)

high_den_output1 <- rows_update(
  est_h_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_h_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_h_5to6 <- act_h %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

high_den_output <- rows_update(
  high_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_h_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(high_den_output,
          '../output/sensitivity analyses/MIT_lower_H_combined.csv')

rm(act_h_1to4)
rm(est_h_to_merge)
rm(high_den_output1)
rm(act_h_5to6)
rm(act_h)
rm(est_h)
```
  
  
### Very high model run

**Estimated yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-veryhighrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_veryhigh-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_v_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-lower-sens-analy-MIT-veryhighrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_lower_veryhigh-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_v_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)
 
rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r lower-sens-analy-MIT-veryhighrun-combine}
# Read in the ECOMOD output files.
est_v <- read.csv('../output/sensitivity analyses/MIT_lower_veryhigh-run_est.csv', 
                  header=T)
# The 'actual' file only has rows containing spring oats
act_v <- read.csv('../output/sensitivity analyses/MIT_lower_veryhigh-run_act.csv', 
                  header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_v_1to4 <- act_v %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_v_to_merge <- est_v %>% 
  dplyr::select(!Field_no)

vhigh_den_output1 <- rows_update(
  est_v_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_v_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_v_5to6 <- act_v %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

vhigh_den_output <- rows_update(
  vhigh_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_v_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(vhigh_den_output,
          '../output/sensitivity analyses/MIT_lower_V_combined.csv')

rm(act_v_1to4)
rm(est_v_to_merge)
rm(vhigh_den_output1)
rm(act_v_5to6)
rm(act_v)
rm(est_v)
```
  
  
## Sensitivity analysis - upper limits to yield penalties
  
Run input files through ECOMOD
  
### Low/absent model run

**Estimated yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-lowrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_low-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_l_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)
  # 52 secs

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-lowrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_low-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_l_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r upper-sens-analy-MIT-lowrun-combine}
# Read in the ECOMOD output files.
est_l <- read.csv("../output/sensitivity analyses/MIT_upper_low-run_est.csv", 
                  header=T)
# The 'actual' file only has rows containing spring oats
act_l <- read.csv('../output/sensitivity analyses/MIT_upper_low-run_act.csv', 
                  header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_l_1to4 <- act_l %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_l_to_merge <- est_l %>% 
  dplyr::select(!Field_no)

low_den_output1 <- rows_update(
  est_l_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_l_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_l_5to6 <- act_l %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

low_den_output <- rows_update(
  low_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_l_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(low_den_output,
          '../output/sensitivity analyses/MIT_upper_L_combined.csv')

rm(act_l_1to4)
rm(est_l_to_merge)
rm(low_den_output1)
rm(act_l_5to6)
rm(act_l)
rm(est_l)
```
  
  
### Medium model run

**Estimated yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-medrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_med-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_m_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-medrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_med-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_m_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)
 
rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r upper-sens-analy-MIT-medrun-combine}
# Read in the ECOMOD output files.
est_m <- read.csv('../output/sensitivity analyses/MIT_upper_med-run_est.csv', header=T)
# The 'actual' file only has rows containing spring oats
act_m <- read.csv('../output/sensitivity analyses/MIT_upper_med-run_act.csv', header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_m_1to4 <- act_m %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_m_to_merge <- est_m %>% 
  dplyr::select(!Field_no)

med_den_output1 <- rows_update(
  est_m_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_m_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_m_5to6 <- act_m %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

med_den_output <- rows_update(
  med_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_m_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(med_den_output,
          '../output/sensitivity analyses/MIT_upper_M_combined.csv')

rm(act_m_1to4)
rm(est_m_to_merge)
rm(med_den_output1)
rm(act_m_5to6)
rm(mit_m_act)
rm(mit_m_est)
rm(act_m)
rm(est_m)
```
  
  
### High model run

**Estimated yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-highrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_high-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_h_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-highrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_high-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_h_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r upper-sens-analy-MIT-highrun-combine}
# Read in the ECOMOD output files.
est_h <- read.csv('../output/sensitivity analyses/MIT_upper_high-run_est.csv', 
                  header=T)
# The 'actual' file only has rows containing spring oats
act_h <- read.csv('../output/sensitivity analyses/MIT_upper_high-run_act.csv', 
                  header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_h_1to4 <- act_h %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_h_to_merge <- est_h %>% 
  dplyr::select(!Field_no)

high_den_output1 <- rows_update(
  est_h_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_h_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_h_5to6 <- act_h %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

high_den_output <- rows_update(
  high_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_h_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(high_den_output,
          '../output/sensitivity analyses/MIT_upper_H_combined.csv')

rm(act_h_1to4)
rm(est_h_to_merge)
rm(high_den_output1)
rm(act_h_5to6)
rm(act_h)
rm(est_h)
```
  
  
### Very high model run

**Estimated yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-veryhighrun-estimatedyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_veryhigh-run_est.csv" 

# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_v_est %>% 
  dplyr::mutate_at(vars(crop1:crop6), 
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

**Actual yield.**
```{r run-ECOMOD-upper-sens-analy-MIT-veryhighrun-actualyield}
# name the output file
fn = "../output/sensitivity analyses/MIT_upper_veryhigh-run_act.csv"

# Set up input file (only need to run the rows containing spring oats).
# Replace spring oats with spring barley and ensure soil is to two decimal 
# places or ECOMOD won't run.
fd = mit_v_act %>% 
  # Extract just the spring oats rows:
  dplyr::filter_all(any_vars(grepl("springoats", .))) %>% 
  # Replace spring oats with spring barley, otherwise ECOMOD won't run:
  dplyr::mutate_at(vars(crop1:crop6),
            list(~recode(.,"springoats" = "springbarley"))) %>% 
  data.frame()
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_act(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="actual",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)
 
rm(fn)
rm(fd)
rm(mfm)
```

Now add the 'actual' spring oat output into the 'estimated' output file.
```{r upper-sens-analy-MIT-veryhighrun-combine}
# Read in the ECOMOD output files.
est_v <- read.csv('../output/sensitivity analyses/MIT_upper_veryhigh-run_est.csv', 
                  header=T)
# The 'actual' file only has rows containing spring oats
act_v <- read.csv('../output/sensitivity analyses/MIT_upper_veryhigh-run_act.csv', 
                  header=T) 

# Extract rows 1-4 to deal with those first
# For these rows, spring oats is the 4th crop and was run as spring barley
act_v_1to4 <- act_v %>% 
  dplyr::filter(Field_no %in% c(1,2,3,4)) %>% 
  dplyr::select(!Field_no)

est_v_to_merge <- est_v %>% 
  dplyr::select(!Field_no)

vhigh_den_output1 <- rows_update(
  est_v_to_merge,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_v_1to4, field_name, totalrotgrossprof, ends_with("4")),
  by = "field_name"
)

act_v_5to6 <- act_v %>% 
  dplyr::filter(Field_no %in% c(5,6)) %>% 
  dplyr::select(!Field_no)

vhigh_den_output <- rows_update(
  vhigh_den_output1,
  ## use only the columns from df2 that you want to update
  ## plus the joining column
  dplyr::select(act_v_5to6, field_name, totalrotgrossprof, ends_with("5")),
  by = "field_name"
)

write.csv(vhigh_den_output,
          '../output/sensitivity analyses/MIT_upper_V_combined.csv')

rm(act_v_1to4)
rm(est_v_to_merge)
rm(vhigh_den_output1)
rm(act_v_5to6)
rm(act_v)
rm(est_v)
```
      

## BAU scenario

Once the data is read in I'll need to insert the additional scenarios that Rob G can run. He can differentiate between low and medium, and high and very high density states:  
* LD-LR becomes LD-LR and MD-LR  
* LD-HR becomes LD-HR and MD-HR  
* HD-HR becomes HD-HR and VD-HR  
  
Read in the raw BAU data.
```{r BAU-raw-data}
bau_econdata = read_xlsx("../data/InputData_BAU_ECOMOD&CFT_2021-12-02.xlsx",5) %>% 
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) %>%  # soil texture needs 2 decimal places
  # replace density and resistance abbreviations with even shorter forms:
  mutate(
    farm_id = gsub('L-Dsty.L-Res', 'LD-LR', farm_id), 
    farm_id = gsub('L-Dsty.H-Res', 'LD-HR', farm_id),
    farm_id = gsub('H-Dsty.H-Res', 'HD-HR', farm_id),
    farm_id = gsub('\\.', '_', farm_id), # replace . with _
  )
```

Insert the additional rows for the differentiated density states.
```{r}
# make a new dataframe with the missing density states
bau_insert.df <- bau_econdata %>% 
  mutate(
    farm_id = gsub('LD-LR', 'MD-LR', farm_id), # replace LD-LR with MD-LR
    farm_id = gsub('LD-HR', 'MD-HR', farm_id), # replace LD-HR with MD-HR
    farm_id = gsub('HD-HR', 'VD-HR', farm_id)  # replace HD-HR with VD-HR
  )
    
# join the two data frames
bau_out.df <- rbind(bau_econdata, bau_insert.df)

# re-order so that new rows are inserted every other row
n <- nrow(bau_econdata)
bau_econ.input.data <- bau_out.df[kronecker(1:n, c(0, n), "+"), ]

rm(bau_econdata, bau_out.df, bau_insert.df)
```


Create input files for each black-grass density state.
```{r BAU-create-input-files}
# LOW / ABSENT
bau_l <- bau_econ.input.data %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>%
  data.frame()

# MEDIUM
bau_m <- bau_l %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

# HIGH
bau_h = bau_m %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "medium", "high"))) %>% 
  data.frame()

# VERY HIGH
bau_v = bau_h %>%
  mutate(across(starts_with('blackgrass'), ~replace(., . %in% "high", "veryhigh"))) %>% 
  data.frame()
```

## Sensitivity analysis - lower limits to yield penalties
  
Run input files through ECOMOD.
  
### Low/absent model run

```{r run-ECOMOD-lower-sens-analy-MIT-lowrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_lower_low-run.csv" 
fd = bau_l
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Medium model run

```{r run-ECOMOD-lower-sens-analy-BAU-medrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_lower_med-run.csv"
fd = bau_m
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

  
### High model run

```{r run-ECOMOD-lower-sens-analy-BAU-highrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_lower_high-run.csv"
fd = bau_h
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Very high model run

```{r run-ECOMOD-lower-sens-analy-BAU-veryhighrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_lower_veryhigh-run.csv"
fd = bau_v
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```


## Sensitivity analysis - upper limits to yield penalties
  
Run input files through ECOMOD.
  
### Low/absent model run

```{r run-ECOMOD-upper-sens-analy-MIT-lowrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_upper_low-run.csv" 
fd = bau_l
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Medium model run

```{r run-ECOMOD-upper-sens-analy-BAU-medrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_upper_med-run.csv"
fd = bau_m
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

  
### High model run

```{r run-ECOMOD-upper-sens-analy-BAU-highrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_upper_high-run.csv"
fd = bau_h
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Very high model run

```{r run-ECOMOD-upper-sens-analy-BAU-veryhighrun}
# name the output file
fn = "../output/sensitivity analyses/BAU_upper_veryhigh-run.csv"
fd = bau_v
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```


## CWW scenario

Once the data is read in I'll need to insert the additional scenarios that Rob G can run. He can differentiate between low and medium, and high and very high density states:  
* LD-LR becomes LD-LR and MD-LR  
* LD-HR becomes LD-HR and MD-HR  
* HD-HR becomes HD-HR and VD-HR  
  
Read in the raw CWW data.
```{r CWW-raw-data}
cww_econdata = read_xlsx("../data/InputData_CWW_ECOMOD&CFT_2021-12-02.xlsx",5) %>% 
  mutate(soil = as.numeric(soil)) %>% # soil texture should be numeric
  mutate_at(3, round, 2) %>%  # soil texture needs 2 decimal places
  # replace density and resistance abbreviations with even shorter forms:
  mutate(
    farm_id = gsub('L-Dsty.L-Res', 'LD-LR', farm_id), 
    farm_id = gsub('L-Dsty.H-Res', 'LD-HR', farm_id),
    farm_id = gsub('H-Dsty.H-Res', 'HD-HR', farm_id),
    farm_id = gsub('\\.', '_', farm_id), # replace . with _
  )
```

Insert the additional rows for the differentiated density states.
```{r CWW-insert-extra-initdenres}
# make a new dataframe with the missing density states
cww_insert.df <- cww_econdata %>% 
  mutate(
    farm_id = gsub('LD-LR', 'MD-LR', farm_id), # replace LD-LR with MD-LR
    farm_id = gsub('LD-HR', 'MD-HR', farm_id), # replace LD-HR with MD-HR
    farm_id = gsub('HD-HR', 'VD-HR', farm_id)  # replace HD-HR with VD-HR
  )
    
# join the two data frames
cww_out.df <- rbind(cww_econdata, cww_insert.df)

# re-order so that new rows are inserted every other row
rm(n)
n <- nrow(cww_econdata)
cww_econ.input.data <- cww_out.df[kronecker(1:n, c(0, n), "+"), ]

rm(cww_econdata, cww_out.df, cww_insert.df)
```

Create input files for each black-grass density state.
```{r CWW-create-input-files}
# LOW / ABSENT
cww_l <- cww_econ.input.data %>%
  mutate(across(starts_with('blackgrass'), 
                ~replace(., . %in% c("medium","high","veryhigh"), "low"))) %>%
  data.frame()

# MEDIUM
cww_m <- cww_l %>%
  mutate(across(starts_with('blackgrass'), 
                ~replace(., . %in% "low", "medium"))) %>% 
  data.frame()

# HIGH
cww_h = cww_m %>%
  mutate(across(starts_with('blackgrass'), 
                ~replace(., . %in% "medium", "high"))) %>% 
  data.frame()

# VERY HIGH
cww_v = cww_h %>%
  mutate(across(starts_with('blackgrass'), 
                ~replace(., . %in% "high", "veryhigh"))) %>% 
  data.frame()
```

## Sensitivity analysis - lower limits to yield penalties
  
Run input files through ECOMOD.
  
### Low/absent model run
```{r CWW-lower--run-ECOMOD-lowrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_lower_low-run.csv" 
fd = cww_l
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Medium model run
```{r CWW-lower--run-ECOMOD-medrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_lower_med-run.csv"
fd = cww_m
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### High model run
```{r CWW-lower--run-ECOMOD-highrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_lower_high-run.csv"
fd = cww_h
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Very high model run
```{r CWW-lower--run-ECOMOD-veryhighrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_lower_veryhigh-run.csv"
fd = cww_v
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_l_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```


## Sensitivity analysis - upper limits to yield penalties
  
Run input files through ECOMOD.
  
### Low/absent model run
```{r CWW-upper--run-ECOMOD-lowrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_upper_low-run.csv" 
fd = cww_l
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Medium model run
```{r CWW-upper--run-ECOMOD-medrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_upper_med-run.csv"
fd = cww_m
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### High model run
```{r CWW-upper--run-ECOMOD-highrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_upper_high-run.csv"
fd = cww_h
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

### Very high model run
```{r CWW-upper--run-ECOMOD-veryhighrun}
# name the output file
fn = "../output/sensitivity analyses/CWW_upper_veryhigh-run.csv"
fd = cww_v
fd$soil = as.numeric(format(round(as.numeric(fd$soil), 2), nsmall = 2))

# Run ECOMOD
mfm = solve_BGRI_ECOMOD_u_est(
  filename=fn,
  farmdata=fd,
  default=NULL,farm="multiple",soil=2.5,
  rotlength=6,rotprob=1/6,
  crops,tillages,seedrate,delsowing,Nfert,Pfert,Kfert,
  bgherbdose,glyphosatedose,numberofsprays,subsidy="yes",
  blackgrass,cropprice,cropyield,yieldoption="estimate",
  Nfertprice,Pfertprice,Kfertprice,seedprice,
  herbprice,glyphosateprice,machsize,fuelprice,labourwage)

rm(fn)
rm(fd)
rm(mfm)
```

