---
title: "Sensitivity analyses 05. Plots and tables"
author: "Alexa Varah"
date: "14/02/2022"
output: html_document
---

# 1. Set up
## 1.1. Load packages
```{r load-packages, message = FALSE}
rm(list=ls())
library(tidyverse) # for data manipulation; includes dplyr, ggplot & more
library(patchwork) # for panel plots
```

## 1.2. Load functions
Function to count complete observations
```{r}
nobs <- function(x) length(x[!is.na(x)])
```
  
## 1.3. Load data
```{r load-data}
# main model run
econ_3DR <- read.csv("../output/economic_data_for_analysis_3DR.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed, 
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))

ww_3DR <- read.csv("../output/wwyield_data_for_analysis_3DR.csv", header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario, levels = c("BAU", "MIT", "CWW")),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))

# sensitivity analysis
econ_3DR_SA <- read.csv("../output/sensitivity analyses/economic_data_for_analysis_3DR_SA.csv", 
                     header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))

ww_3DR_SA <- read.csv("../output/sensitivity analyses/wwyield_data_for_analysis_3DR_SA.csv", 
                     header = T) %>% 
  dplyr::mutate(
    scenario = factor(scenario),
    region = factor(region, levels = c("north", "central", "east")),
    soiltype = factor(soiltype, levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                                  levels = c("LD-LR", "LD-HR", "HD-HR")))
```

# 2. Summarise and join
```{r}
# main model run
econ_rotmean <- econ_3DR %>% 
  group_by(scenario, region, soiltype, initdenres_collapsed) %>% # grouping factor for sum
  dplyr::mutate(
    # gross profit           
    gp = mean(wtd_gp_mean),
    gp_ci_l = gp - (1.96 * (sd(wtd_gp_mean) / sqrt(nobs(wtd_gp_mean)))),
    gp_ci_u = gp + (1.96 * (sd(wtd_gp_mean) / sqrt(nobs(wtd_gp_mean)))),
    # opportunity cost
    oc = mean(wtd_opp_cost_mean),
    oc_ci_l = oc - 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean)))),
    oc_ci_u = oc + 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, region, soiltype, initdenres_collapsed, .keep_all = TRUE) %>% 
  dplyr::select(scenario, region, soiltype, initdenres_collapsed, gp:oc_ci_u) %>% 
  dplyr::mutate(sensanaly = "no") %>% 
  dplyr::relocate(sensanaly)

ww_rotmean <- ww_3DR %>% 
  group_by(scenario, region, soiltype, initdenres_collapsed) %>% # grouping factor for sum
  dplyr::mutate(
    # wheat yield           
    ww = mean(ww_yield_mean),
    ww_ci_l = mean(ww_yield_mean) - (1.96 * (sd(ww_yield_mean) / sqrt(nobs(ww_yield_mean)))),
    ww_ci_u = mean(ww_yield_mean) + (1.96 * (sd(ww_yield_mean) / sqrt(nobs(ww_yield_mean)))),
    # productivity cost
    pc = mean(prod_cost_mean),
    pc_ci_l = mean(prod_cost_mean) - 
      (1.96 * (sd(prod_cost_mean) / sqrt(length(prod_cost_mean)))),
    pc_ci_u = mean(prod_cost_mean) + 
      (1.96 * (sd(prod_cost_mean) / sqrt(length(prod_cost_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, region, soiltype, initdenres_collapsed, .keep_all = TRUE) %>% 
  dplyr::select(scenario, region, soiltype, initdenres_collapsed, ww:pc_ci_u) %>% 
  dplyr::mutate(sensanaly = "no") %>% 
  dplyr::relocate(sensanaly)

# sensitivity analysis
econ_rotmean_SA <- econ_3DR_SA %>% 
  group_by(scenario, region, soiltype, initdenres_collapsed, sensanaly) %>% # grouping factor for sum
  dplyr::mutate(
    # gross profit           
    gp = mean(wtd_gp_mean),
    gp_ci_l = gp - (1.96 * (sd(wtd_gp_mean) / sqrt(nobs(wtd_gp_mean)))),
    gp_ci_u = gp + (1.96 * (sd(wtd_gp_mean) / sqrt(nobs(wtd_gp_mean)))),
    # opportunity cost
    oc = mean(wtd_opp_cost_mean),
    oc_ci_l = oc - 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean)))),
    oc_ci_u = oc + 
      (1.96 * (sd(wtd_opp_cost_mean) / sqrt(length(wtd_opp_cost_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, region, soiltype, initdenres_collapsed, sensanaly, .keep_all = TRUE) %>% 
  dplyr::select(sensanaly, scenario, region, soiltype, initdenres_collapsed, gp:oc_ci_u)

ww_rotmean_SA <- ww_3DR_SA %>% 
  group_by(scenario, region, soiltype, initdenres_collapsed, sensanaly) %>% # grouping factor for sum
  dplyr::mutate(
    # wheat yield           
    ww = mean(ww_yield_mean),
    ww_ci_l = mean(ww_yield_mean) - (1.96 * (sd(ww_yield_mean) / sqrt(nobs(ww_yield_mean)))),
    ww_ci_u = mean(ww_yield_mean) + (1.96 * (sd(ww_yield_mean) / sqrt(nobs(ww_yield_mean)))),
    # productivity cost
    pc = mean(prod_cost_mean),
    pc_ci_l = mean(prod_cost_mean) - 
      (1.96 * (sd(prod_cost_mean) / sqrt(length(prod_cost_mean)))),
    pc_ci_u = mean(prod_cost_mean) + 
      (1.96 * (sd(prod_cost_mean) / sqrt(length(prod_cost_mean))))
    ) %>% 
  # retain only one row per scenario-year:
  distinct(scenario, region, soiltype, initdenres_collapsed, sensanaly, .keep_all = TRUE) %>% 
  dplyr::select(sensanaly, scenario, region, soiltype, initdenres_collapsed, ww:pc_ci_u)
```


Join data.
```{r}
gp_oc <- rbind(econ_rotmean, econ_rotmean_SA)  %>% 
  # Make new column combining scenario and sensitivity analysis
  dplyr::mutate(
    ID = paste(scenario, sensanaly, sep = "_")
  ) %>% 
  # Remove '_no' from this column
  dplyr::mutate(
    ID = gsub('_no', '', ID) 
  ) %>% 
  dplyr::relocate(ID) %>% 
  # Ensure factor levels are in the order we want
  mutate(
    scenario = factor(scenario),
    region = factor(region,
                    levels = c("north", "central","east")),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                        levels = c("LD-LR", "LD-HR", "HD-HR")),
    ID = factor(ID,
                levels = c("BAU_lower", "BAU", "BAU_upper",
                           "MIT_lower", "MIT", "MIT_upper",
                           "CWW_lower", "CWW", "CWW_upper")),
    scenario = factor(scenario,
                      levels = c("BAU", "MIT", "CWW"))
  ) %>% 
  dplyr::relocate(sensanaly)

ww_pc <- rbind(ww_rotmean, ww_rotmean_SA)  %>% 
  # Make new column combining scenario and sensitivity analysis
  dplyr::mutate(
    ID = paste(scenario, sensanaly, sep = "_")
  ) %>% 
  # Remove '_no' from this column
  dplyr::mutate(
    ID = gsub('_no', '', ID) 
  ) %>% 
  dplyr::relocate(ID) %>% 
  # Ensure factor levels are in the order we want
  mutate(
    scenario = factor(scenario),
    region = factor(region,
                    levels = c("north", "central","east")),
    soiltype = factor(soiltype,
                      levels = c("heavy", "medium","light")),
    initdenres_collapsed = factor(initdenres_collapsed,
                        levels = c("LD-LR", "LD-HR", "HD-HR")),
    ID = factor(ID,
                levels = c("BAU_lower", "BAU", "BAU_upper",
                           "MIT_lower", "MIT", "MIT_upper",
                           "CWW_lower", "CWW", "CWW_upper")),
    scenario = factor(scenario,
                      levels = c("BAU", "MIT", "CWW"))
  ) %>% 
  dplyr::relocate(sensanaly)
```

Save data for plot.
```{r}
write.csv(gp_oc, "../output/data for sensitivity analysis scatter_OC.csv", 
          row.names = FALSE)

write.csv(ww_pc, "../output/data for sensitivity analysis scatter_PC.csv", 
          row.names = FALSE)
```


# 4. Plot economic data
## 4.1. Scatter plot, gp all scenarios

First, specify the labels for the panels.  
```{r specify-panel-labels}
region.labs <- c("Northern England", "Central England", "Eastern England") # new
names(region.labs) <- c("north", "central", "east") # original

soiltype.labs <- c("Heavy soil", "Medium soil", "Light soil") # new
names(soiltype.labs) <- c("heavy", "medium", "light") # original
```

Then specify the plot.
```{r plot-gp-sensanaly}
plot1 <- ggplot(gp_oc, aes(initdenres_collapsed, gp, colour = ID, shape = ID)) + 
  facet_grid(region ~ soiltype,
             labeller = labeller(region = region.labs, 
                                 soiltype = soiltype.labs)
  ) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(x = "Initial density and resistance", 
       y = "Mean annual gross profit (£/ha)") +
  # specify colours for 'scenario':
  scale_color_manual(name = "Scenario & 
yield penalties",
                     values = c("#88CCEE", # BAU, lower yield penalty
                                "#005FCC", # BAU
                                "#00306F", # BAU, upper yield penalty
                                
                                "#DDCC77", # MIT, lower yield penalty
                                "#999933", # MIT
                                "#117733", # MIT, upper yield penalty
                                
                                "#CC6677", # CWW, lower yield penalty
                                "#882255", # CWW
                                "#AA4499"  # CWW, upper yield penalty
                                )) + 
  scale_shape_manual(name = "Scenario & 
yield penalties",
                     values=c(15, 15, 15,    # BAU 15 = square
                              16, 16, 16,    # MIT 16 = circle
                              17, 17, 17)) + # CWW 17 = triangle
  theme(strip.placement = 'outside',
        strip.text.x = element_text(size = 14),
        strip.text.y = element_text(size = 14),
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(size=rel(1.5)), 
        axis.text.y=element_text(size=rel(1.5)),
        legend.title=element_text(size=18),
        legend.text=element_text(size=14)
        
  ) +
  geom_pointrange(aes(ymin = gp_ci_l, 
                      ymax = gp_ci_u),
                  position=position_dodge(.8)
  ) 

plot1
```

Save plot.
```{r save-plot1, eval = FALSE, echo=FALSE}
#ggsave("figures/SensAnaly_Gross profit.png", height = 10, width = 10)

png("../figures/SA_05_gp by initcondit_all scenarios.png",
    height = 10, width = 10, units = "in", res = 300)
print(plot1)
dev.off()
```


## 4.2. Scatter plot, gp, MIT & BAU

If not done above, specify the labels for the panels.  
```{r specify-panel-labels}
region.labs <- c("Northern England", "Central England", "Eastern England") # new
names(region.labs) <- c("north", "central", "east") # original

soiltype.labs <- c("Heavy soil", "Medium soil", "Light soil") # new
names(soiltype.labs) <- c("heavy", "medium", "light") # original
```

Then specify the plot.
```{r plot-gp-sensanaly-noCWW}
plot2 <- ggplot(gp_oc %>% filter(!scenario=="CWW"), 
                aes(initdenres_collapsed, gp, 
                    colour = ID, shape = ID)) + 
  facet_grid(region ~ soiltype,
             labeller = labeller(region = region.labs, 
                                 soiltype = soiltype.labs)
  ) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(x = "Initial density and resistance", 
       y = "Mean annual gross profit (£/ha)") +
  # specify colours for 'scenario':
  scale_color_manual(name = "Scenario & 
yield penalties",
                     values = c("#88CCEE", # BAU, lower yield penalty
                                "#005FCC", # BAU
                                "#00306F", # BAU, upper yield penalty
                                
                                "#DDCC77", # MIT, lower yield penalty
                                "#999933", # MIT
                                "#117733" # MIT, upper yield penalty
                                )) + 
  scale_shape_manual(name = "Scenario & 
yield penalties",
                     values=c(15, 15, 15,    # BAU 15 = square
                              16, 16, 16)) + # MIT 16 = circle
  theme(strip.placement = 'outside',
        strip.text.x = element_text(size = 16),
        strip.text.y = element_text(size = 16),
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(size=rel(1.7)),
        axis.text.y=element_text(size=rel(1.7)),
        legend.title=element_text(size=18),
        legend.text=element_text(size=16)
        
  ) +
  geom_pointrange(aes(ymin = gp_ci_l, 
                      ymax = gp_ci_u), 
                  position=position_dodge(width=0.6),
                  size = 0.9) 

plot2
```

Save plot.
```{r save-econ-plot-noCWW}
#ggsave("figures/SA_05_gp by initcondit_BAU & MIT.png", height = 10, width = 10)

png("../figures/SA_05_gp by initcondit_BAU & MIT.png",
    height = 10, width = 10, units = "in", res = 300)
print(plot2)
dev.off()
```

# 5. Plot yield data

If not done above, specify the labels for the panels.  
```{r specify-panel-labels}
region.labs <- c("Northern England", "Central England", "Eastern England") # new
names(region.labs) <- c("north", "central", "east") # original

soiltype.labs <- c("Heavy soil", "Medium soil", "Light soil") # new
names(soiltype.labs) <- c("heavy", "medium", "light") # original
```

Then specify the plot.
```{r plot-gp-sensanaly-noCWW}
plot3 <- ggplot(ww_pc %>% filter(!scenario=="CWW"), 
                aes(initdenres_collapsed, ww, 
                    colour = ID, shape = ID)) + 
  facet_grid(region ~ soiltype,
             labeller = labeller(region = region.labs, 
                                 soiltype = soiltype.labs)
  ) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(x = "Initial density and resistance", 
       y = "Mean annual wheat yield (t/ha)") +
  # specify colours for 'scenario':
  scale_color_manual(name = "Scenario & 
yield penalties",
                     values = c("#88CCEE", # BAU, lower yield penalty
                                "#005FCC", # BAU
                                "#00306F", # BAU, upper yield penalty
                                
                                "#DDCC77", # MIT, lower yield penalty
                                "#999933", # MIT
                                "#117733" # MIT, upper yield penalty
                                )) + 
  scale_shape_manual(name = "Scenario & 
yield penalties",
                     values=c(15, 15, 15,    # BAU 15 = square
                              16, 16, 16)) + # MIT 16 = circle
  theme(strip.placement = 'outside',
        strip.text.x = element_text(size = 16),
        strip.text.y = element_text(size = 16),
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(size=rel(1.7)),
        axis.text.y=element_text(size=rel(1.7)),
        legend.title=element_text(size=18),
        legend.text=element_text(size=16)
        
  ) +
  geom_pointrange(aes(ymin = ww_ci_l, 
                      ymax = ww_ci_u), 
                  position=position_dodge(width=0.6),
                  size = 0.9) 

plot3
```


Save plot.
```{r save-yield-plot-noCWW}
#ggsave("figures/SA_05_gp by initcondit_BAU & MIT.png", height = 10, width = 10)

png("../figures/SA_05_ww by initcondit_BAU & MIT.png",
    height = 10, width = 10, units = "in", res = 300)
print(plot3)
dev.off()
```

# 6. Panel plot

Remove legend from plot of gross profit.
```{r plot-gp-sensanaly-noCWW-nolegend}
plot2_noleg <- ggplot(gp_oc %>% filter(!scenario=="CWW"), 
                aes(initdenres_collapsed, gp, 
                    colour = ID, shape = ID)) + 
  facet_grid(region ~ soiltype,
             labeller = labeller(region = region.labs, 
                                 soiltype = soiltype.labs)
  ) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(x = "Initial density and resistance", 
       y = "Mean annual gross profit (£/ha)") +
  # specify colours for 'scenario':
  scale_color_manual(name = "Scenario & 
yield penalties",
                     values = c("#88CCEE", # BAU, lower yield penalty
                                "#005FCC", # BAU
                                "#00306F", # BAU, upper yield penalty
                                
                                "#DDCC77", # MIT, lower yield penalty
                                "#999933", # MIT
                                "#117733" # MIT, upper yield penalty
                                )) + 
  scale_shape_manual(name = "Scenario & 
yield penalties",
                     values=c(15, 15, 15,    # BAU 15 = square
                              16, 16, 16)) + # MIT 16 = circle
  theme(strip.placement = 'outside',
        strip.text.x = element_text(size = 16),
        strip.text.y = element_text(size = 16),
        plot.title = element_text(size=22),
        axis.title=element_text(size=18),
        axis.text.x=element_text(size=rel(1.7)),
        axis.text.y=element_text(size=rel(1.7)),
        legend.title=element_text(size=18),
        legend.text=element_text(size=16)
        
  ) +
  geom_pointrange(aes(ymin = gp_ci_l, 
                      ymax = gp_ci_u), 
                  position=position_dodge(width=0.6),
                  size = 0.9) +
  theme(legend.position="none")

plot2_noleg
```


```{r panel-plot}
SA_gp_ww <- (plot2_noleg + plot3) + 
  plot_annotation(tag_levels = 'a', tag_prefix = '(',  tag_suffix = ')') & 
  theme(plot.tag = element_text(size = 18, face="bold"))
SA_gp_ww
```

Save plot.
```{r}
png("../figures/SA_05_gp and ww.png",
    height = 10, width = 20, units = "in", res = 300)
print(SA_gp_ww)
dev.off()
```