---
title: "Sensitivity Analyses - Estimate weighted winter wheat and summarise"
author: "Alexa Varah"
date: "2023-02-16"
output: html_document
---

# 1. Intro / rationale

This script manipulates ECOMOD output files to create data frames that can be used for analysis. I calculate the weighted winter wheat yield for a field. This is done by weighting by the proportion of squares in each density state. Other crop yields are not weighted as in ECOMOD they don't respond to black-grass density.  

# 2. Load packages
```{r load-packages}
rm(list=ls())
library(tidyverse) # for easy data manipulation; includes dplyr, ggplot & more
library(gmodels) # to calculate 95% CIs
```


# 3. Load and tidy data
## 3.1. Load & prep ECOMOD data
### 3.1.1. Lower limits of yield penalty
#### MIT, lower
Load data.
```{r MIT-lower--Load-economic-data}
# Low density model run
mit_low_l <- read.csv("../output/sensitivity analyses/MIT_lower_L_combined.csv", 
                    header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Medium density model run
mit_med_l <- read.csv("../output/sensitivity analyses/MIT_lower_M_combined.csv", 
                    header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# High density model run
mit_high_l <- read.csv("../output/sensitivity analyses/MIT_lower_H_combined.csv", 
                     header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Very high density model run
mit_vhig_l <- read.csv("../output/sensitivity analyses/MIT_lower_V_combined.csv", 
                     header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()
```

Convert ECOMOD output to long-format and join data frames together.
```{r MIT-lower--Reshape-economic-data}
## Low density model run
mit_low_l <- reshape(mit_low_l, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run

## Medium density model run
mit_med_l <- reshape(mit_med_l, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run

## High density model run
mit_high_l <- reshape(mit_high_l, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run

## Very high density model run
mit_vhig_l <- reshape(mit_vhig_l, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run

## Join data frames.
mit_economicdata_lower <- rbind(mit_low_l, mit_med_l, mit_high_l, mit_vhig_l)
```

Create an 'initcondit' variable in the economic data set that is in the same format as in the simulated density data. The 'initcondit' variable combines English region, soil type and initial density and resistance state, e.g. n_h_VD-HR.   
I also need to a column on which to join the economic and density data frames This needs to identify initial conditions and year in the rotation.  
```{r MIT-lower--Make-initcondit-&-joinID}
mit_econdata_lower <- mit_economicdata_lower %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::rename(year = rotation) %>% 
  mutate(
    field_name = gsub('\\.', '_', field_name), # replace . with _
    initdenres = sub('_.*', '', field_name), # extract chrs before first '_'
    soiltype = sub('.*\\_', '', field_name), # extract chrs after last '_'
    region = substr(field_name, start = 7, stop = 7), # extract 7th character
    region = tolower(region),
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "mit",
    joinID = paste(scenario, initcondit, year, sep = "_"),
    sensanaly = "lower"
    ) %>% 
  dplyr::relocate(joinID, scenario, modelrun, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name)
```

Clean up. 
```{r}
rm(mit_low_l)
rm(mit_med_l)
rm(mit_high_l)
rm(mit_vhig_l)
rm(mit_economicdata_lower)
```


#### BAU, lower
Load data.
```{r BAU-lower--Load-economic-data}
# Low density model run
bau_low_l <- read.csv("../output/sensitivity analyses/BAU_lower_low-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Medium density model run
bau_med_l <- read.csv("../output/sensitivity analyses/BAU_lower_med-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# High density model run
bau_high_l <- read.csv("../output/sensitivity analyses/BAU_lower_high-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Very high density model run
bau_vhig_l <- read.csv("../output/sensitivity analyses/BAU_lower_veryhigh-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()
```

Convert ECOMOD output to long-format and join data frames together.
```{r BAU-lower--Reshape-economic-data}
## Low density model run
bau_low_l <- reshape(bau_low_l, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run

## Medium density model run
bau_med_l <- reshape(bau_med_l, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run

## High density model run
bau_high_l <- reshape(bau_high_l, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run

## Very high density model run
bau_vhig_l <- reshape(bau_vhig_l, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run

## Join data frames.
bau_economicdata_lower <- rbind(bau_low_l, bau_med_l, bau_high_l, bau_vhig_l)
```

Create an 'initcondit' variable in the economic data set that is in the same format as in the simulated density data. The 'initcondit' variable combines English region, soil type and initial density and resistance state, e.g. n_h_VD-HR.   
I also need to a column on which to join the economic and density data frames This needs to identify initial conditions and year in the rotation.  
```{r BAU-lower--Make-initcondit-&-joinID}
bau_econdata_lower <- bau_economicdata_lower %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::rename(year = rotation) %>% 
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
    
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),

    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "bau",
    joinID = paste(scenario, initcondit, year, sep = "_"),
    sensanaly = "lower"
  ) %>% 
  dplyr::relocate(joinID, scenario, modelrun, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name)
```

Clean up.
```{r}
## Clean up.
rm(bau_low_l)
rm(bau_med_l)
rm(bau_high_l)
rm(bau_vhig_l)
rm(bau_economicdata_lower)
```
  
  
#### CWW, lower
Load data.
```{r CWW-lower--Load-economic-data}
# Low density model run
cww_low_l <- read.csv("../output/sensitivity analyses/CWW_lower_low-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Medium density model run
cww_med_l <- read.csv("../output/sensitivity analyses/CWW_lower_med-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# High density model run
cww_high_l <- read.csv("../output/sensitivity analyses/CWW_lower_high-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Very high density model run
cww_vhig_l <- read.csv("../output/sensitivity analyses/CWW_lower_veryhigh-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()
```

Convert ECOMOD output to long-format and join data frames together.
```{r CWW-lower--Reshape-economic-data}
## Low density model run
cww_low_l <- reshape(cww_low_l, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run

## Medium density model run
cww_med_l <- reshape(cww_med_l, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run

## High density model run
cww_high_l <- reshape(cww_high_l, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run

## Very high density model run
cww_vhig_l <- reshape(cww_vhig_l, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run

## Join data frames.
cww_economicdata_lower <- rbind(cww_low_l, cww_med_l, cww_high_l, cww_vhig_l)
```

Create an 'initcondit' variable in the economic data set that is in the same format as in the simulated density data. The 'initcondit' variable combines English region, soil type and initial density and resistance state, e.g. n_h_VD-HR.   
I also need to a column on which to join the economic and density data frames This needs to identify initial conditions and year in the rotation.  
```{r CWW-lower--Make-initcondit-&-joinID}
cww_econdata_lower <- cww_economicdata_lower %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::rename(year = rotation) %>% 
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
    
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),

    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "cww",
    joinID = paste(scenario, initcondit, year, sep = "_"),
    sensanaly = "lower"
  ) %>% 
  dplyr::relocate(joinID, scenario, modelrun, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name)
```

Clean up.
```{r}
## Clean up.
rm(cww_low_l)
rm(cww_med_l)
rm(cww_high_l)
rm(cww_vhig_l)
rm(cww_economicdata_lower)
```



### 3.1.2. Upper limits of yield penalty
#### MIT, upper
Load data.
```{r MIT-upper--Load-economic-data}
# Low density model run
mit_low_u <- read.csv("../output/sensitivity analyses/MIT_upper_L_combined.csv", 
                    header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Medium density model run
mit_med_u <- read.csv("../output/sensitivity analyses/MIT_upper_M_combined.csv", 
                    header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# High density model run
mit_high_u <- read.csv("../output/sensitivity analyses/MIT_upper_H_combined.csv", 
                     header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Very high density model run
mit_vhig_u <- read.csv("../output/sensitivity analyses/MIT_upper_V_combined.csv", 
                     header=TRUE) %>% 
  select(-X) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()
```

Convert ECOMOD output to long-format and join data frames together.
```{r MIT-upper--Reshape-economic-data}
## Low density model run
mit_low_u <- reshape(mit_low_u, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run

## Medium density model run
mit_med_u <- reshape(mit_med_u, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run

## High density model run
mit_high_u <- reshape(mit_high_u, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run

## Very high density model run
mit_vhig_u <- reshape(mit_vhig_u, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run

## Join data frames.
mit_economicdata_upper <- rbind(mit_low_u, mit_med_u, mit_high_u, mit_vhig_u)
```

Create an 'initcondit' variable in the economic data set that is in the same format as in the simulated density data. The 'initcondit' variable combines English region, soil type and initial density and resistance state, e.g. n_h_VD-HR.   
I also need to a column on which to join the economic and density data frames This needs to identify initial conditions and year in the rotation.  
```{r MIT-upper--Make-initcondit-&-joinID}
mit_econdata_upper <- mit_economicdata_upper %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::rename(year = rotation) %>% 
  mutate(
    field_name = gsub('\\.', '_', field_name), # replace . with _
    initdenres = sub('_.*', '', field_name), # extract chrs before first '_'
    soiltype = sub('.*\\_', '', field_name), # extract chrs after last '_'
    region = substr(field_name, start = 7, stop = 7), # extract 7th character
    region = tolower(region),
    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "mit",
    joinID = paste(scenario, initcondit, year, sep = "_"),
    sensanaly = "upper"
    ) %>% 
  dplyr::relocate(joinID, scenario, modelrun, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name)
```

Clean up. 
```{r}
rm(mit_low_u)
rm(mit_med_u)
rm(mit_high_u)
rm(mit_vhig_u)
rm(mit_economicdata_upper)
```


#### BAU, upper
Load data.
```{r BAU-upper--Load-economic-data}
# Low density model run
bau_low_u <- read.csv("../output/sensitivity analyses/BAU_upper_low-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Medium density model run
bau_med_u <- read.csv("../output/sensitivity analyses/BAU_upper_med-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# High density model run
bau_high_u <- read.csv("../output/sensitivity analyses/BAU_upper_high-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Very high density model run
bau_vhig_u <- read.csv("../output/sensitivity analyses/BAU_upper_veryhigh-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()
```

Convert ECOMOD output to long-format and join data frames together.
```{r BAU-upper--Reshape-economic-data}
## Low density model run
bau_low_u <- reshape(bau_low_u, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run

## Medium density model run
bau_med_u <- reshape(bau_med_u, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run

## High density model run
bau_high_u <- reshape(bau_high_u, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run

## Very high density model run
bau_vhig_u <- reshape(bau_vhig_u, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run

## Join data frames.
bau_economicdata_upper <- rbind(bau_low_u, bau_med_u, bau_high_u, bau_vhig_u)
```

Create an 'initcondit' variable in the economic data set that is in the same format as in the simulated density data. The 'initcondit' variable combines English region, soil type and initial density and resistance state, e.g. n_h_VD-HR.   
I also need to a column on which to join the economic and density data frames This needs to identify initial conditions and year in the rotation.  
```{r BAU-upper--Make-initcondit-&-joinID}
bau_econdata_upper <- bau_economicdata_upper %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::rename(year = rotation) %>% 
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
    
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),

    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "bau",
    joinID = paste(scenario, initcondit, year, sep = "_"),
    sensanaly = "upper"
  ) %>% 
  dplyr::relocate(joinID, scenario, modelrun, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name)
```

Clean up.
```{r}
## Clean up.
rm(bau_low_u)
rm(bau_med_u)
rm(bau_high_u)
rm(bau_vhig_u)
rm(bau_economicdata_upper)
```
  
  
#### CWW, upper
Load data.
```{r CWW-upper--Load-economic-data}
# Low density model run
cww_low_u <- read.csv("../output/sensitivity analyses/CWW_upper_low-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Medium density model run
cww_med_u <- read.csv("../output/sensitivity analyses/CWW_upper_med-run.csv", 
                    header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# High density model run
cww_high_u <- read.csv("../output/sensitivity analyses/CWW_upper_high-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()

# Very high density model run
cww_vhig_u <- read.csv("../output/sensitivity analyses/CWW_upper_veryhigh-run.csv", 
                     header=TRUE) %>% 
  select(-Field_no) %>% # remove extra column added by R when reading in the file
  rename_with(stringr::str_replace, # add '.' b4 the number in 'crop' colnames
              pattern = "crop", replacement = "crop.", 
              matches("crop")) %>% 
  rename(meanrotgrossprof = totalrotgrossprof) %>% 
  data.frame()
```

Convert ECOMOD output to long-format and join data frames together.
```{r CWW-upper--Reshape-economic-data}
## Low density model run
cww_low_u <- reshape(cww_low_u, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "low") # add a column to indicate the model run

## Medium density model run
cww_med_u <- reshape(cww_med_u, varying=c(2:85), direction="long", 
                  idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "medium") # add a column to indicate the model run

## High density model run
cww_high_u <- reshape(cww_high_u, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "high") # add a column to indicate the model run

## Very high density model run
cww_vhig_u <- reshape(cww_vhig_u, varying=c(2:85), direction="long", 
                   idvar = "field_name", sep = ".", timevar = "rotation") %>% 
  arrange(field_name) %>% 
  mutate(modelrun = "veryhigh") # add a column to indicate the model run

## Join data frames.
cww_economicdata_upper <- rbind(cww_low_u, cww_med_u, cww_high_u, cww_vhig_u)
```

Create an 'initcondit' variable in the economic data set that is in the same format as in the simulated density data. The 'initcondit' variable combines English region, soil type and initial density and resistance state, e.g. n_h_VD-HR.   
I also need to a column on which to join the economic and density data frames This needs to identify initial conditions and year in the rotation.  
```{r CWW-upper--Make-initcondit-&-joinID}
cww_econdata_upper <- cww_economicdata_upper %>% 
  dplyr::select(-meanrotgrossprof) %>% 
  dplyr::rename(year = rotation) %>% 
  dplyr::mutate(
    initdenres = sub('.*\\_', '', field_name), # extract chrs after last '_'
    
    # extract characters between 1st and 2nd underscore ( x[2] pulls out the 
    # 2nd split string when split on underscores):
    soiltype = sapply(strsplit(field_name, "_"), function(x) x[2]), 
    soiltype = substr(soiltype, start = 1, stop = 1), # extract 1st character
    
    region = sub('_.*', '', field_name), # extract chrs before first '_'
    region = tolower(region),

    initcondit = paste(region, soiltype, initdenres, sep = "_"),
    scenario = "cww",
    joinID = paste(scenario, initcondit, year, sep = "_"),
    sensanaly = "upper"
  ) %>% 
  dplyr::relocate(joinID, scenario, modelrun, initcondit, 
                  initdenres, region, soiltype) %>% 
  dplyr::select(-field_name)
```

Clean up.
```{r}
## Clean up.
rm(cww_low_u)
rm(cww_med_u)
rm(cww_high_u)
rm(cww_vhig_u)
rm(cww_economicdata_upper)
```




### 3.1.3. Join all economic scenarios & tidy
Now join all the economic data together before calculating weighted gross profit.
```{r make-ridy-economic-data}
econdata <- rbind(bau_econdata_lower,
                   bau_econdata_upper,
                   cww_econdata_lower,
                   cww_econdata_upper,
                   mit_econdata_lower,
                   mit_econdata_upper) %>% 
  relocate(sensanaly, .before = scenario) %>% 
  dplyr::mutate(scenario = toupper(scenario),
                #joinID = str_replace_all(joinID, "mit","MIT"),
                #joinID = str_replace_all(joinID, "bau","BAU"),
                #joinID = str_replace_all(joinID, "cww","CWW"),
                joinID = str_replace_all(joinID, c("mit" = "MIT", "bau" = "BAU", "cww" = "CWW")),
                region = str_replace_all(region, c("e" = "east", "n" = "north", "c" = "central")), # NB e first
                soiltype = str_replace_all(soiltype, c("h" = "heavy", "m" = "medium", "l" = "light"))
                ) 
```


## 3.2. Load simulated density data
Load the tidied simulation data. Combine the 'a' and 'l' columns as I don't differentiate between black-grass being absent and being low density in ECOMOD. Add a column that is identical in both the economic and simulation data frames, and which identifies scenario, initial conditions and year.
```{r load-density-data}
simdata <- readRDS(file = "../output/simulation_results_tidy.rds") %>%
  # sum the proportions of absent and low density black-grass
  rowwise() %>% 
  dplyr::mutate(al = sum(c_across(a:l), na.rm = T)) %>% # new category: absent & low
  ungroup() %>% 
  # new ID on which to join this data frame with the economic data
  dplyr::mutate(joinID = paste(scenario, initcondit, year, sep="_"))  
```


# 4. Calculate weighted values
## 4.1. Calculate
To do this, join the simulated density-resistance data and the economic data.

Only winter wheat yield will vary depending on black-grass density; yield of all other crops will be unaffected by the weighting process. I calculate weighted yield, fuel cost, labour cost and operations cost. Fuel, labour and operations costs all involve using work rates in their calculation. Work rate is a function of crop yield and so these variables  will be affected by black-grass density when the crop is wheat. When you do the join, the `econdata` rows will automatically repeat to fill the 37 iterations present in `simdata`.  

Not all variables need to be weighted as they are not all affected by crop yield and will therefore not respond to changes in BG density. Furthermore, even weighted variables won't always show differences between imputations as at low and medium densities, black-grass doesn't affect yield (although as Rob G simulates density distributions, fields with low density will still have some grid cells in high density and so this will affect yield).  
  
Opportunity cost is calculated as CWW-BAU or MIT-BAU. In other words, BAU is the foregone strategy and the farmer has switched to an alternative strategy. This means that negative values indicate BAU had higher gross profit, so the other scenario makes the farmer less money.

```{r calculate-weighted-values}
yield_allimp_SA <- left_join(simdata %>% dplyr::select(joinID, imp, al, m, h, v),
                          econdata, 
                          by="joinID") %>% 
  # Calculate weighted yield for each row for the affected variables
  dplyr::mutate(
    wtd_yield = case_when(
      modelrun == "low" ~ al*yield,
      modelrun == "medium" ~ m*yield,
      modelrun == "high" ~ h*yield,
      modelrun == "veryhigh" ~ v*yield
    )
  ) %>%
  # Add weighted variables across model runs (low, med, high & vhigh den) 
  # to get total yield etc (i.e. add the contributions from the 
  # different densities in different parts of the field) for each year of each 
  # strategy (ID), and for each imputation of that year-strategy (imp).
  dplyr::group_by(imp, joinID, sensanaly) %>% 
  dplyr::mutate(wtd_yield = sum(wtd_yield)) %>% 
  dplyr::select(imp, sensanaly, joinID, scenario, initdenres, initcondit,
                region, soiltype, year, crop, wtd_yield) %>% 
  dplyr::distinct(imp, sensanaly, joinID, .keep_all = TRUE) %>% 
  # re-specify formats and order of levels:
  dplyr::mutate( 
    scenario = factor(scenario, levels=c("BAU", "MIT", "CWW")),
    region = factor(region, levels=c("north", "central", "east")),
    soiltype = factor(soiltype, levels=c("heavy", "medium", "light")),
    year = as.integer(year),
    initdenres = factor(initdenres, levels = c("LD-LR", "LD-HR", "MD-LR",
                                               "MD-HR", "HD-HR", "VD-HR")),
    initcondit = factor(initcondit, levels = c(
      "n_h_VD-HR", "n_m_VD-HR", "n_l_VD-HR", 
      "c_h_VD-HR", "c_m_VD-HR", "c_l_VD-HR",
      "e_h_VD-HR", "e_m_VD-HR", "e_l_VD-HR",
      
      "n_h_HD-HR", "n_m_HD-HR", "n_l_HD-HR",
      "c_h_HD-HR", "c_m_HD-HR", "c_l_HD-HR",
      "e_h_HD-HR", "e_m_HD-HR", "e_l_HD-HR",
      
      "n_h_MD-HR", "n_m_MD-HR", "n_l_MD-HR",
      "c_h_MD-HR", "c_m_MD-HR", "c_l_MD-HR",
      "e_h_MD-HR", "e_m_MD-HR", "e_l_MD-HR",
      
      "n_h_MD-LR", "n_m_MD-LR", "n_l_MD-LR",
      "c_h_MD-LR", "c_m_MD-LR", "c_l_MD-LR",
      "e_h_MD-LR", "e_m_MD-LR", "e_l_MD-LR",
      
      "n_h_LD-HR", "n_m_LD-HR", "n_l_LD-HR",
      "c_h_LD-HR", "c_m_LD-HR", "c_l_LD-HR",
      "e_h_LD-HR", "e_m_LD-HR", "e_l_LD-HR",
      
      "n_h_LD-LR", "n_m_LD-LR", "n_l_LD-LR",
      "c_h_LD-LR", "c_m_LD-LR", "c_l_LD-LR",
      "e_h_LD-LR", "e_m_LD-LR", "e_l_LD-LR"))
  ) %>% 
  dplyr::rename(ID = joinID) %>% 
  # calculate productivity cost of switching out of BAU
  # first, for any crop that isn't wheat, assign zero yield
  dplyr::mutate(ww_yield = ifelse(stringr::str_detect(crop,'wheat'),wtd_yield,0)) %>% 
  group_by(imp, sensanaly, initcondit, year) %>% 
  dplyr::mutate(wtd_prod_cost_ww = ww_yield - ww_yield[scenario == "BAU"]) %>% 
  ungroup() %>% 
  dplyr::arrange(sensanaly, scenario, initdenres, region, soiltype, year) %>% 
  dplyr::relocate(sensanaly)
```

## 4.2. Save output file
```{r}
write.csv(yield_allimp_SA,
          "../output/sensitivity analyses/wwyield_data_for_analysis-all_imputations_SA.csv", 
          row.names = FALSE)

saveRDS(yield_allimp_SA, 
        file = "../output/sensitivity analyses/wwyield_data_for_analysis-all_imputations_SA.rds")
```


## 4.3. Clean up
```{r clean-up, echo=FALSE}
rm(bau_econdata_lower, bau_econdata_upper, 
   cww_econdata_lower, cww_econdata_upper,
   mit_econdata_lower, mit_econdata_upper,
   econdata, simdata)
```


# Session info
```{r}
#sessionInfo()
```

